---
title: "OctCruiseChemistry"
author: "Dylan Titmuss"
date: "3/15/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script visualizes the chemistry data from the October RSA cruise.
Run chunks 1-7 of `Chemistry_Oct.Rmd` to load data.

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, root.dir = "~/Desktop/Repos/ScallopRSA2021")

library(tidyverse)
```

## Temp vs Sal, coloured cast
```{r}
plot <-
ggplot(oct, aes(x = Salinity, y = Temp, shape = Cast, col = Cast)) +
  #geom_point() +
  geom_text(aes(label = Station), size = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  #xlab("Salinity (PSU)") +
  #ylab("Temperature (°C)") +
  #geom_label(aes(x = 35.255, y = 20.1, label = "October"), size = 5, color = "black",
  #           fontface = "bold", label.size = 0.75, label.padding = unit(0.5, "lines")) +
  theme_bw()

library(plotly)
ggplotly(plot)

ggplot(oct, aes(x = Salinity, y = Temp, shape = Cast, col = dDIC)) +
  geom_point() +
  #geom_text(aes(label = Station), size = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_fill_distiller(limits = c(-10, 10), palette = "RdBu",
                       aesthetics = "colour") +
  #xlab("Salinity (PSU)") +
  #ylab("Temperature (°C)") +
  #geom_label(aes(x = 35.255, y = 20.1, label = "October"), size = 5, color = "black",
  #           fontface = "bold", label.size = 0.75, label.padding = unit(0.5, "lines")) +
  #theme_bw() +
  theme(panel.background = element_rect(fill = "black", colour = "black"))
```

## Temp vs Sal, EMs highlighted
```{r}
ggplot(oct, aes(x = Salinity, y = Temp, col = Cast)) +
  geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_point(data = oct[((oct$Station == "005" |
                          oct$Station == "043" |
                          oct$Station == "091") &
                          oct$Cast == "Surface") |
                        ((oct$Station == "009" |
                          oct$Station == "033" |
                          oct$Station == "053") &
                          oct$Cast == "Bottom"), ],
             aes(x = Salinity, y = Temp, shape = Cast),
             col = "darkorchid", size = 6, inherit.aes = FALSE) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  scale_shape_manual(values = c(0, 1), guide = "none") +
  theme_bw()

library(grid)
grid.force()  # make grobs visible to grid editing tools
grid.edit("geom_point.points", grep = TRUE, gp = gpar(lwd = 2))
```

## DIC vs Sal, coloured cast
```{r}
ggplot(oct, aes(x = Salinity, y = DIC, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()

#plot(DIC ~ Salinity, data = oct, col = factor(Cast))
#identify(oct$DIC ~ oct$Salinity)
```

## TA vs Sal, coloured cast
```{r}
plot <- ggplot(oct, aes(x = Salinity, y = TA, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()

ggplotly(plot)

#plot(TA ~ Salinity, data = oct, col = factor(Cast))
#abline(lm(oct$TA ~ oct$Salinity))
#identify(oct$TA ~ oct$Salinity)

### check 096, 098, 100 bottom TA + sal
```

## TA vs DIC, coloured cast
```{r}
plot <-
oct %>%
filter(Cast == "Surface") %>%
ggplot(aes(x = DIC, y = TA, shape = Cast, col = Cast)) +
  #geom_point() +
  geom_text(aes(label = Station), size = 2) +
  #scale_shape_manual(values = c(16, 1),
  scale_shape_manual(values = 1,
                     guide = guide_legend(reverse = TRUE)) +
  #scale_colour_manual(values = c("darkblue", "coral2"),
  scale_colour_manual(values = "coral2",
                      guide = guide_legend(reverse = TRUE)) +
  xlim(1960, 2030) +
  ylim(2180, 2285) +
  theme_bw()

ggplotly(plot)

#plot(oct$TA ~ oct$DIC, col = factor(oct$Cast))
#identify(oct$TA ~ oct$DIC)
```

## DIC vs density, coloured cast
```{r}
ggplot(oct, aes(x = Density, y = DIC, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## TA vs density, coloured cast
```{r}
ggplot(oct, aes(x = Density, y = TA, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## Connect surface & bottom points with lines
```{r}
ggplot(oct, aes(x = Density, y = TA, shape = Cast, col = Cast, group = Station)) +
  geom_point() +
  geom_line(col = "grey56", linetype = "dotted") +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()

ggplot(oct, aes(x = Salinity, y = DIC, shape = Cast, col = Cast, group = Station)) +
  geom_point() +
  geom_line(col = "grey56", linetype = "dotted") +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()

ggplot(oct, aes(x = Density, y = DIC, shape = Cast, col = Cast, group = Station)) +
  geom_point() +
  geom_line(col = "grey56", linetype = "dotted") +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()

ggplot(oct, aes(x = Salinity, y = TA, shape = Cast, col = Cast, group = Station)) +
  geom_point() +
  geom_line(col = "grey56", linetype = "dotted") +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()

ggplot(oct, aes(x = Salinity, y = Temp, shape = Cast, col = Cast, group = Station)) +
  geom_point() +
  geom_line(col = "grey56", linetype = "dotted") +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## Oct + May together
Run chunks 2-7 of `Chemistry_May.Rmd` to load May data.
```{r}
# Temp vs Sal, coloured season
ggplot() +
  geom_point(data = may, aes(x = Salinity, y = Temp, shape = Cast, col = "May")) +
  geom_point(data = oct, aes(x = Salinity, y = Temp, shape = Cast, col = "October")) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  xlab("Salinity (PSU)") +
  ylab("Temperature (°C)") +
  theme_bw()

# DIC vs Sal, coloured season
ggplot() +
  geom_point(data = may, aes(x = Salinity, y = DIC, shape = Cast, col = "May")) +
  geom_point(data = oct, aes(x = Salinity, y = DIC, shape = Cast, col = "October")) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  xlab("Salinity (PSU)") +
  ylab("DIC (umol/kg)") +
  theme_bw()

# TA vs Sal, coloured season
ggplot() +
  geom_point(data = may, aes(x = Salinity, y = TA, shape = Cast, col = "May")) +
  geom_point(data = oct, aes(x = Salinity, y = TA, shape = Cast, col = "October")) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  xlab("Salinity (PSU)") +
  ylab("Total Alkalinity (umol/kg)") +
  theme_bw()

# DIC vs rho, coloured season
ggplot() +
  geom_point(data = may, aes(x = Density, y = DIC, shape = Cast, col = "May")) +
  geom_point(data = oct, aes(x = Density, y = DIC, shape = Cast, col = "October")) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  xlab("Density (kg/m^3)") +
  ylab("DIC (umol/kg)") +
  theme_bw()

# TA vs rho, coloured season
ggplot() +
  geom_point(data = may, aes(x = Density, y = TA, shape = Cast, col = "May")) +
  geom_point(data = oct, aes(x = Density, y = TA, shape = Cast, col = "October")) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  xlab("Density (kg/m^3)") +
  ylab("Total Alkalinity (umol/kg)") +
  theme_bw()

# TA vs DIC, coloured season
ggplot() +
  geom_point(data = may, aes(x = DIC, y = TA, shape = Cast, col = "May")) +
  geom_point(data = oct, aes(x = DIC, y = TA, shape = Cast, col = "October")) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  xlab("DIC (umol/kg)") +
  ylab("Total Alkalinity (umol/kg)") +
  theme_bw()
```

## Plot delta values
```{r}
oct %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 2) +
  geom_abline(slope = -17/106) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  theme_bw()

# negative DIC means DIC < expected --> photosynth signal
  # combination of photosynth & calcification/precipitation
# positive DIC means DIC > expected --> respiration signal
  # combination of respiration & dissolution

# positive TA is combination of dissolution & photosynthesis
# negative TA is combination of calcification/precipitation & respiration

# surface
oct %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast, col = pCO2)) + # color by pCO2
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 2) +
  geom_abline(slope = -17/106) +
  scale_shape_manual(values = 1) +
  scale_colour_viridis(limits = c(330, 510), option = "magma") +
  theme_bw()
```

## pCO2 & flux prop-prop plots
```{r}
oct %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = pCO2, y = flux)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 420, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(1)) +
  theme_bw()

oct %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = Temp, y = pCO2)) +
  geom_point(aes(shape = Cast)) +
  scale_shape_manual(values = c(1)) +
  theme_bw()
```

## Plot AOU data
```{r}
oct %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast, col = AOU)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 2) +
  geom_abline(slope = -17/106) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_color_viridis(option = "magma") +
  theme_bw()

# dDIC vs AOU
oct %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = AOU, shape = Cast, col = Cast)) +
    geom_point() +
    #geom_text(aes(label = as.integer(Station)), size = 3) +
    geom_point(data = oct[((oct$Station == "009" |
                            oct$Station == "033" |
                            oct$Station == "053") &
                            oct$Cast == "Bottom"), ],
               col = "red", size = 3) +
    scale_colour_manual(values = "darkblue") +
    theme_bw() +
    theme(legend.position = "none") + 
    geom_vline(xintercept = 0, linetype = 2) +
    geom_hline(yintercept = 0, linetype = 2)

oct.bottom <- oct %>%
  filter(Cast == "Bottom")

lm(oct.bottom$AOU ~ oct.bottom$dDIC) # slope = 0.4223

ggplot(oct, aes(x = AOU, y = dDIC, shape = Cast)) +
  geom_point() +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 0.768) +   # 106/138
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

lm(oct.bottom$dDIC ~ oct.bottom$AOU) # 0.505

# dTA vs AOU
ggplot(oct, aes(x = AOU, y = dTA, shape = Cast)) +
  geom_point() +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = -0.123) +   # -17/138   # negative for AOU
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

lm(oct.bottom$dTA ~ oct.bottom$AOU) # -0.1142

# AOU vs Sal
ggplot(oct, aes(x = Salinity, y = AOU, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkblue", "coral2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## Visualize DO prop-prop
```{r}
oct %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast, col = dDO)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_color_viridis(option = "magma") +
  theme_bw()

oct %>%
  #filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = dDO)) +
  geom_point(aes(shape = Cast)) +
  #geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = -106/138) +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

oct %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = DIC, y = DO)) +
  #geom_point(aes(shape = Cast)) +
  geom_text(aes(label = as.integer(Station)), size = 3) +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

oct %>%
  ggplot(aes(x = dTA, y = dDO)) +
  geom_point(aes(shape = Cast)) +
  #geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

oct %>%
  ggplot(aes(x = dDO, y = AOU)) +
  geom_point(aes(shape = Cast)) +
  #geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()
```

## Plot "other" components
```{r}
oct %>%
  ggplot(aes(x = DIC.other, y = TA.other)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  theme_bw()

oct %>%
  ggplot(aes(x = DIC.other, y = TA.other)) +
  geom_point(aes(shape = Cast, col = AOU)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_color_viridis(option = "viridis") +
  theme_bw()

oct %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = DIC.other, y = dDO)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## Delta plots
```{r}
ggplot() +
  geom_point(data = oct, aes(x = dDIC, y = dTA, shape = Cast, col = "Oct")) +
  #geom_errorbar(data = oct, aes(x = dDIC, y = dTA,
  #                              xmin = dDIC - sdDICn, xmax = dDIC + sdDICn),
  #              col = "royalblue", alpha = 0.3, width = 1) +
  #geom_errorbar(data = oct, aes(x = dDIC, y = dTA,
  #                              ymin = dTA - sdTAn, ymax = dTA + sdTAn),
  #              col = "royalblue", alpha = 0.3, width = 1) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = -median(oct$sdDICn, na.rm = T),
           xmax = median(oct$sdDICn, na.rm = T),
           ymin = -Inf,
           ymax = Inf) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = -Inf,
           xmax = -median(oct$sdDICn, na.rm = T),
           ymin = -median(oct$sdTAn, na.rm = T),
           ymax = median(oct$sdTAn, na.rm = T)) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = median(oct$sdDICn, na.rm = T),
           xmax = Inf,
           ymin = -median(oct$sdTAn, na.rm = T),
           ymax = median(oct$sdTAn, na.rm = T)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 2) +
  geom_abline(slope = -17/106) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = "royalblue",
                      name = "Month") +
  theme_bw()

# negative DIC means DIC < expected --> photosynth signal
  # combination of photosynth & calcification/precipitation
# positive DIC means DIC > expected --> respiration signal
  # combination of respiration & dissolution

# positive TA is combination of dissolution & photosynthesis
# negative TA is combination of calcification/precipitation & respiration

# surface
ggplot() +
  geom_point(data = may[which(may$Cast == "Surface"), ],
             aes(x = dDIC, y = dTA, shape = Cast, col = "May")) +
  geom_point(data = oct[which(oct$Cast == "Surface"), ],
             aes(x = dDIC, y = dTA, shape = Cast, col = "Oct")) +
  #geom_text(data = may[which(may$Cast == "Surface"), ],
  #           aes(x = dDIC, y = dTA, label = Station, col = "May")) +
  #geom_text(data = oct[which(oct$Cast == "Surface"), ],
  #           aes(x = dDIC, y = dTA, label = Station, col = "Oct")) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 2) +
  geom_abline(slope = -17/106) +
  scale_shape_manual(values = c(1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  theme_bw()

# bottom
ggplot() +
  geom_point(data = may[which(may$Cast == "Bottom"), ],
             aes(x = dDIC, y = dTA, shape = Cast, col = "May")) +
  geom_point(data = oct[which(oct$Cast == "Bottom"), ],
             aes(x = dDIC, y = dTA, shape = Cast, col = "Oct")) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 2) +
  geom_abline(slope = -17/106) +
  scale_shape_manual(values = c(16),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("chartreuse3", "royalblue"),
                      name = "Month") +
  xlim(-20, 86) +
  guides(shape = guide_legend(order = 1),
         col = guide_legend(order = 2)) +
  theme_bw()

# dDO plots
ggplot() +
  geom_point(data = oct, aes(x = dDIC, y = dDO, shape = Cast, col = "Oct")) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = -median(oct$sdDICn, na.rm = T),
           xmax = median(oct$sdDICn, na.rm = T),
           ymin = -Inf,
           ymax = Inf) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = -Inf,
           xmax = -median(oct$sdDICn, na.rm = T),
           ymin = -median(oct$sdDOn, na.rm = T),
           ymax = median(oct$sdDOn, na.rm = T)) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = median(oct$sdDICn, na.rm = T),
           xmax = Inf,
           ymin = -median(oct$sdDOn, na.rm = T),
           ymax = median(oct$sdDOn, na.rm = T)) +
  #geom_text(data = may, aes(x = dDIC, y = dDO, label = Station , col = "May")) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = -138/106) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = "royalblue",
                      name = "Month") +
  theme_bw()

ggplot() +
  geom_point(data = oct, aes(x = dTA, y = dDO, shape = Cast, col = "Oct")) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = -median(oct$sdTAn, na.rm = T),
           xmax = median(oct$sdTAn, na.rm = T),
           ymin = -Inf,
           ymax = Inf) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = -Inf,
           xmax = -median(oct$sdTAn, na.rm = T),
           ymin = -median(oct$sdDOn, na.rm = T),
           ymax = median(oct$sdDOn, na.rm = T)) +
  annotate("rect", alpha = 0.2, fill = "royalblue",
           xmin = median(oct$sdTAn, na.rm = T),
           xmax = Inf,
           ymin = -median(oct$sdDOn, na.rm = T),
           ymax = median(oct$sdDOn, na.rm = T)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = -138/-17) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = "royalblue",
                      name = "Month") +
  theme_bw()
```



















## Temp v Sal, coloured by 3rd property
```{r}
#ggplot_build(plot)$layout$panel_scales_x[[1]]$range$range # [31.5991 35.6009]
#ggplot_build(plot)$layout$panel_scales_y[[1]]$range$range # [8.317186 20.698551]

# bottom, coloured depth
oct %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = Salinity, y = Temp, col = Depth)) +
  geom_point() +
  scale_colour_viridis(option = "mako", direction = -1) +
  scale_x_continuous(limits = c(31.59, 35.61)) +
  scale_y_continuous(limits = c(8.31, 20.70)) +
  guides(colour = guide_colourbar(reverse = TRUE)) + 
  theme_bw()

#plot(Temp ~ Salinity, data = oct)
#identify(oct$Temp ~ oct$Salinity)

# coloured DIC
ggplot(oct, aes(x = Salinity, y = Temp, col = DIC, shape = Cast)) +
  geom_point() +
  scale_colour_viridis(option = "rocket") +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

#plot(Temp ~ Salinity, data = oct, col = factor(DIC))
#identify(oct$Temp ~ oct$Salinity)

### already checked 009 bottom DIC -- fine

# coloured TA
ggplot(oct, aes(x = Salinity, y = Temp, col = TA, shape = Cast)) +
  geom_point() +
  scale_colour_viridis(option = "mako") +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

# coloured pH
ggplot(oct, aes(x = Salinity, y = Temp, col = pH, shape = Cast)) +
  geom_point() +
  scale_colour_viridis(name = "pH") +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

# coloured OmegaAragonite
ggplot(oct, aes(x = Salinity, y = Temp, col = OmegaAragonite, shape = Cast)) +
  geom_point() +
  scale_colour_viridis(name = "OmegaAragonite") +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

# coloured density
ggplot(oct, aes(x = Salinity, y = Temp, col = Density, shape = Cast)) +
  geom_point() +
  scale_colour_viridis(name = "Density") +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()
```

