---
title: "MayCruiseChemistry"
author: "Dylan Titmuss"
date: "1/19/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script visualizes the chemistry data from the May RSA cruise.
Run chunks 1-7 of `Chemistry_May.Rmd` to load data.

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, root.dir = "~/Desktop/Repos/ScallopRSA2021")

library(tidyverse)
```

## Temp vs Sal, coloured cast
```{r}
ggplot(may, aes(x = Salinity, y = Temp, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkslateblue", "brown2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## Temp vs Sal, EMs highlighted
```{r}
ggplot(may, aes(x = Salinity, y = Temp, col = Cast)) +
  geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_point(data = may[((may$Station == "004" |
                          may$Station == "072" |
                          may$Station == "113") &
                          may$Cast == "Surface") |
                        ((may$Station == "001" |
                          may$Station == "004" |
                          may$Station == "113" |
                          may$Station == "059") &
                          may$Cast == "Bottom"), ],
             aes(x = Salinity, y = Temp, shape = Cast),
             col = "darkorchid", size = 6, inherit.aes = FALSE) +
  scale_colour_manual(values = c("darkslateblue", "brown2"),
                      guide = guide_legend(reverse = TRUE)) +
  scale_shape_manual(values = c(0, 1), guide = "none") +
  theme_bw()

library(grid)
grid.force()  # make grobs visible to grid editing tools
grid.edit("geom_point.points", grep = TRUE, gp = gpar(lwd = 2))
```

## DIC vs Sal, coloured cast
```{r}
ggplot(may, aes(x = Salinity, y = DIC, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkslateblue", "brown2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## TA vs Sal, coloured cast
```{r}
ggplot(may, aes(x = Salinity, y = TA, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkslateblue", "brown2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## TA vs DIC, coloured cast
```{r}
ggplot(may, aes(x = DIC, y = TA, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkslateblue", "brown2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## DIC vs density, coloured cast
```{r}
ggplot(may, aes(x = Density, y = DIC, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkslateblue", "brown2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## TA vs density, coloured cast
```{r}
ggplot(may, aes(x = Density, y = TA, shape = Cast, col = Cast)) +
  geom_point() +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = c("darkslateblue", "brown2"),
                      guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```

## Plot delta values
```{r}
may %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(intercept = 0, slope = 2) +
  geom_abline(intercept = 0, slope = -17/106) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  xlim(-41, 33) +
  theme_bw()

# negative DIC means DIC < expected --> photosynth signal
  # combination of photosynth & calcification/precipitation
# positive DIC means DIC > expected --> respiration signal
  # combination of respiration & dissolution

# positive TA is combination of dissolution & photosynthesis
# negative TA is combination of calcification/precipitation & respiration

# surface
may %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast, col = pCO2)) + # color by pCO2
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(intercept = 0, slope = 2) +
  geom_abline(intercept = 0, slope = -17/106) +
  scale_shape_manual(values = 1) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()
```

## pCO2 & flux prop-prop plots
```{r}
may %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = pCO2, y = flux)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 420, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(1)) +
  theme_bw()

may %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = Temp, y = pCO2)) +
  geom_point(aes(shape = Cast)) +
  scale_shape_manual(values = c(1)) +
  theme_bw()
```

## Plot AOU data
```{r}
may %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast, col = AOU)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(intercept = 0, slope = 2) +
  geom_abline(intercept = 0, slope = -17/106) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_color_viridis(option = "magma") +
  theme_bw()

# dDIC vs AOU
may %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = AOU, shape = Cast, col = Cast)) +
    geom_point() +
    #geom_text(aes(label = as.integer(Station)), size = 3) +
    geom_point(data = may[((may$Station == "009" |
                            may$Station == "033" |
                            may$Station == "053") &
                            may$Cast == "Bottom"), ],
               col = "red", size = 3) +
    scale_colour_manual(values = "darkblue") +
    theme_bw() +
    theme(legend.position = "none") + 
    geom_vline(xintercept = 0, linetype = 2) +
    geom_hline(yintercept = 0, linetype = 2)

may.bottom <- may %>%
  filter(Cast == "Bottom")

lm(may.bottom$AOU ~ may.bottom$dDIC) # slope = 0.5526

ggplot(may, aes(x = AOU, y = dDIC, shape = Cast)) +
  geom_point() +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = 0.768) +   # 106/138
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

lm(may.bottom$dDIC ~ may.bottom$AOU) # 0.6113

# dTA vs AOU
ggplot(may, aes(x = AOU, y = dTA, shape = Cast)) +
  geom_point() +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(slope = -0.123) +   # -17/138   # negative for AOU
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()

lm(may.bottom$dTA ~ may.bottom$AOU) # -0.07876
```

## Visualize DO prop-prop
```{r}
may %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = dTA)) +
  geom_point(aes(shape = Cast, col = dDO)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_color_viridis(option = "magma") +
  theme_bw()

may %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDIC, y = dDO)) +
  geom_point(aes(shape = Cast)) +
  #geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16)) +
  theme_bw()

may %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dTA, y = dDO)) +
  geom_point(aes(shape = Cast)) +
  #geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16)) +
  theme_bw()

may %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = dDO, y = AOU)) +
  geom_point(aes(shape = Cast)) +
  #geom_text(aes(label = as.integer(Station)), size = 3) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16)) +
  theme_bw()
```

## Plot "other" components
```{r}
may %>%
  ggplot(aes(x = DIC.other, y = TA.other)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  theme_bw()

may %>%
  ggplot(aes(x = DIC.other, y = TA.other)) +
  geom_point(aes(shape = Cast, col = AOU)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_color_viridis(option = "viridis") +
  theme_bw()

may %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = DIC.other, y = dDO)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  theme_bw()
```
