---
title: "Voronoi_mapping"
author: "Dylan Titmuss"
date: "2023-05-10"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script visualizes the chemistry data from the May sea scallop RSA cruise.
Run chunks 1-5 of `chemistry_May.Rmd` to load data.

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(numform)
library(sf)
library(nngeo)
library(marmap)
library(cowplot)

# for colour scales
library(viridis)
library(pals)
library(rcartocolor)
library(Redmonder)
library(colorspace)

#setwd("~/Desktop/Repos/ScallopRSA2021")
```

## Load data
```{r}
may <- read.csv("./data/MayCruiseData.csv") %>%
  rename(Lat = Latitude_degrees_start,
         Long = Longitude_degrees_start,
         Depth = Depth_m_CTD,
         Temp = Temperature,
         DO = Dissolved_oxygen) %>%
  #select(Date, Station, Cast, Lat, Long,
  #       Depth, Temp, Pressure, SeaPressure, Salinity,
  #       DIC, TA, DO) %>%
  mutate(Station = as.character(f_pad_zero(Station))) # add leading zeros to stations
```

## Convert coordinates from DM to DD
```{r}
chd <- substr(may$Lat, 3, 3)[1]

# latitude
Lat_split_may <- str_split_fixed(may$Lat, chd, 2) %>%
                 as.data.frame()
Lat_split_may$V2 <- str_remove_all(Lat_split_may$V2, pattern = "'") %>%
                    as.numeric()
Lat_split_may$V2 <- Lat_split_may$V2/60
Lat_split_may$V1 <- as.numeric(Lat_split_may$V1)

may$Lat <- Lat_split_may$V1 + Lat_split_may$V2
rm(Lat_split_may)

# longitude
Long_split_may <- str_split_fixed(may$Long, chd, 2) %>%
                  as.data.frame()
Long_split_may$V2 <- str_remove_all(Long_split_may$V2, pattern = "'") %>%
                     as.numeric()
Long_split_may$V2 <- Long_split_may$V2/60
Long_split_may$V1 <- as.numeric(Long_split_may$V1)

may$Long <- -(Long_split_may$V1 + Long_split_may$V2)
rm(Long_split_may)
rm(chd)
```

## FOR MAY ONLY: tweak certain coords to fall within polygon
```{r}
may <- may %>%
  mutate(Long = ifelse(Station == "006", Long + 0.06, Long),
         Lat = ifelse(Station == "026", Lat + 0.02, Lat),
         Long = ifelse(Station == "089", Long - 0.04, Long))
```

## Create simple features object of chem data
```{r}
# create geometry column in data frame from lat/long data
for(i in 1:nrow(may)) {
  may$geometry[i] <- st_point(x = c(may$Long[i], may$Lat[i])) %>%
    st_sfc(crs = 4326)
}

# create an sf object from data frame
station_sf <- st_sf(may, crs = 4326)

bottom_sf <- station_sf %>%
  filter(Cast == "Bottom")

surface_sf <- station_sf %>%
  filter(Cast == "Surface")
```

## Load GB shapefiles
```{r}
GB <- st_read("./data/2020SAMZones/GB_Estimation_Areas_2019_UTM19_PDT_SFModified.shp")

# check CRS
# st_crs(GB)   # EPSG:26919

# check loaded
ggplot() +
  geom_sf(data = GB, fill = NA, linewidth = 0.4, linetype = "dashed") +
  scale_y_continuous(breaks = c(40, 41, 42)) +
  coord_sf(xlim = c(-70.5, -66), ylim = c(40, 42.5), crs = st_crs(4326)) +
  theme_bw() +
  theme(axis.title = element_blank())

# subset shapefile to SAMs
NLS_West <- subset(GB, NewSAMS == "NLS-West") %>%
  fortify()
NLS_North <- subset(GB, NewSAMS == "NLS-North") %>%
  fortify()
NLS_SouthShallow <- subset(GB, NewSAMS == "NLS-South-Shallow") %>%
  fortify()
NLS_SouthDeep <- subset(GB, NewSAMS == "NLS-South-Deep") %>%
  fortify()
GSC <- subset(GB, NewSAMS == "GSC") %>%
  fortify()
CL1_Sliver <- subset(GB, NewSAMS == "CL1-Sliver") %>%
  fortify()
CL1_Access <- subset(GB, NewSAMS == "CL1-Access") %>%
  fortify()
CL1_South <- subset(GB, NewSAMS == "CL1-South") %>%
  fortify()
NF <- subset(GB, NewSAMS == "NF") %>%
  fortify()
CL2_North <- subset(GB, NewSAMS == "CL2-North") %>%
  fortify()
CL2_AccessSoutheast <- subset(GB, NewSAMS == "CL2-Access-Southeast") %>%
  fortify()
CL2_AccessSouthwest <- subset(GB, NewSAMS == "CL2-Access-Southwest") %>%
  fortify()
CL2_Ext <- subset(GB, NewSAMS == "CL2-Ext") %>%
  fortify()
SF_East <- subset(GB, NewSAMS == "SF-East") %>%
  fortify()
SF <- subset(GB, NewSAMS == "SF") %>%
  fortify()

# combine polygons to create unified outline
GB_sf <- st_union(st_geometry(NLS_West), st_geometry(NLS_North)) %>%
  st_union(st_geometry(NLS_SouthShallow)) %>%
  st_union(st_geometry(NLS_SouthDeep)) %>%
  st_union(st_geometry(GSC)) %>%
  st_union(st_geometry(CL1_Sliver)) %>%
  st_union(st_geometry(CL1_Access)) %>%
  st_union(st_geometry(CL1_South)) %>%
  st_union(st_geometry(NF)) %>%
  st_union(st_geometry(CL2_North)) %>%
  st_union(st_geometry(CL2_AccessSoutheast)) %>%
  st_union(st_geometry(CL2_AccessSouthwest)) %>%
  st_union(st_geometry(CL2_Ext)) %>%
  st_union(st_geometry(SF_East)) %>%
  st_union(st_geometry(SF)) %>%
  st_remove_holes() # remove false slivers between polygon borders

# check loaded
ggplot() +
  geom_sf(data = GB_sf, fill = NA, linewidth = 0.4, linetype = "dashed") +
  scale_y_continuous(breaks = c(40, 41, 42)) +
  coord_sf(xlim = c(-70.5, -66), ylim = c(40, 42.5), crs = st_crs(4326)) +
  theme_bw() +
  theme(axis.title = element_blank())
```

## Conduct nearest-neighbor interpolation (Voronoi)
```{r}
bottom_sf_geom <- st_union(bottom_sf) %>%
  st_transform(crs = 26919)
bottom_sf_v <- st_voronoi(bottom_sf_geom)
bottom_sf_v <- st_sf(bottom_sf_v)

surface_sf_geom <- st_union(surface_sf) %>%
  st_transform(crs = 26919)
surface_sf_v <- st_voronoi(surface_sf_geom)
surface_sf_v <- st_sf(surface_sf_v)

# mask Voronoi with contour
bottom_sf_v <- st_intersection(st_cast(bottom_sf_v),
                               st_union(st_buffer(GB, dist = 500)))
bottom_sf_v <- st_sf(bottom_sf_v)

#st_crs(bottom_sf_v)

bottom_sf2 <- bottom_sf %>%
  st_transform(crs = 26919)

surface_sf_v <- st_intersection(st_cast(surface_sf_v),
                                st_union(st_buffer(GB, dist = 500)))
surface_sf_v <- st_sf(surface_sf_v)

#st_crs(surface_sf_v)

surface_sf2 <- surface_sf %>%
  st_transform(crs = 26919)

# complete spatial join
bottom_sf_v2 <- st_join(bottom_sf_v, bottom_sf2)
#glimpse(bottom_sf_v2)
surface_sf_v2 <- st_join(surface_sf_v, surface_sf2)
```

## Create simple features objects for 3 central points
```{r}
bottom_sf3 <- bottom_sf2 %>%
  filter(Station == "033" | Station == "034" | Station == "035")

surface_sf3 <- surface_sf2 %>%
  filter(Station == "033" | Station == "034" | Station == "035")
```

## Load higher-res coastline data
```{r}
# turn off spherical geometry to avoid "duplicate vertex" errors
sf_use_s2(FALSE)

# get Massachusetts coastline
mass <- read_sf("/Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/library/gshhg-shp-2.3.7/GSHHS_shp/f/GSHHS_f_L1.shp") %>%
  st_make_valid() %>%
  st_crop(xmin = -71, xmax = -66, ymin = 40, ymax = 43)
```

## Import bathy data
```{r}
GB_bathy <- getNOAA.bathy(lon1 = -74, lon2 = -62, lat1 = 37, lat2 = 46, resolution = 1)

bathy_xyz <- as.xyz(GB_bathy)

# check import
ggplot() +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               binwidth = 100, alpha = 0.4) +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -50, alpha = 0.2) +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -150, alpha = 0.2) +
  scale_y_continuous(breaks = c(40, 41, 42)) +
  coord_sf(xlim = c(-70.5, -66), ylim = c(40, 42.5), crs = st_crs(4326)) +
  theme_bw() +
  theme(axis.title = element_blank())
```

## Create interpolated map
```{r}
# DIC surface
ggplot() +
  geom_sf(data = surface_sf_v2,
          aes(fill = DIC),
          size = 0.25,
          col = NA) +
  geom_sf(data = surface_sf3,
          aes(col = DIC),
          size = 6,
          shape = 18) +
            # replace the three lines above w/ four lines below to add outline to points, for plots with diverging scales
          #aes(fill = DIC),
          #size = 4,
          #shape = 23,
          #linetype = "dashed") +
    # next line adds GB outline, for plots with diverging scales
  #geom_sf(data = GB_sf, fill = NA, linewidth = 0.4, linetype = "dashed") +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -50, alpha = 0.3, col = "grey50") +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -100, alpha = 0.3, col = "grey50") +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -500, alpha = 0.3, col = "grey50") +
  geom_sf(data = mass, fill = "darkgrey", col = NA) +
  scale_fill_gradientn(limits = c(1970, 2140),
                       colours = parula(100),
                       aesthetics = c("fill", "colour"),
                       name = expression(bold("DIC (μmol kg"^-1*")"))) +
  scale_y_continuous(breaks = c(40, 41, 42)) +
  coord_sf(xlim = c(-70.5, -66), ylim = c(40, 42.5), crs = st_crs(4326)) +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5),
         col = guide_colourbar(title.position = "top", title.hjust = 0.5)) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(face = "bold"),
        legend.position = "bottom",
        legend.key.width = unit(1.7, "cm"),
        legend.text = element_text(angle = 45, vjust = 0.75, size = 10))

# DIC bottom
ggplot() +
  geom_sf(data = bottom_sf_v2,
          aes(fill = DIC),
          size = 0.25,
          colour = NA) +
  geom_sf(data = bottom_sf3,
          aes(fill = DIC),
          size = 4,
          shape = 23,
          linetype = "dashed") +
  geom_sf(data = GB_sf, fill = NA, linewidth = 0.4, linetype = "dashed") +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -50, alpha = 0.3, colour = "grey50") +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -100, alpha = 0.3, colour = "grey50") +
  geom_contour(data = bathy_xyz,
               aes(x = V1, y = V2, z = V3),
               breaks = -500, alpha = 0.3, colour = "grey50") +
  geom_sf(data = mass, fill = "darkgrey", colour = NA) +
  scale_fill_gradientn(limits = c(1970, 2140),
                       colours = parula(100),
                       aesthetics = c("fill", "colour"),
                       name = expression(bold("DIC (μmol kg"^-1*")"))) +
  scale_y_continuous(breaks = c(40, 41, 42)) +
  coord_sf(xlim = c(-70.5, -66), ylim = c(40, 42.5), crs = st_crs(4326)) +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5),
         col = guide_colourbar(title.position = "top", title.hjust = 0.5)) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(face = "bold"),
        legend.position = "bottom",
        legend.key.width = unit(1.7, "cm"),
        legend.text = element_text(angle = 45, vjust = 0.75, size = 10))
```
