---
title: "OctCruiseChemistry"
author: "Dylan Titmuss"
date: "3/15/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script manipulates the chemistry data from the October RSA cruise.

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, root.dir = "~/Desktop/Repos/ScallopRSA2021")

library(tidyverse)
library(numform) # for f_pad_zero()
library(seacarb)
library(gsw) # for AOU
library(viridis)
library(ncdf4)
library(chron)
# download MixSIAR from GitHub; latest changes not yet on CRAN
#remotes::install_github("brianstock/MixSIAR", dependencies = T)
library(MixSIAR)
library(rjags)

setwd("~/Desktop/Repos/ScallopRSA2021")
```

## Load data
```{r}
oct <- read.csv("./data/OctCruiseData.csv") %>%
  rename(Lat = Latitude_degrees_start,
         Long = Longitude_degrees_start,
         Depth = Depth_m_CTD,
         Temp = Temperature,
         DO = Dissolved_oxygen) %>%
  filter(Filtered == "") %>%
  select(Date, Station, Cast, Lat, Long,
         Depth, Temp, Pressure, SeaPressure, Salinity,
         DIC, TA, DO) %>%
  mutate(Station = as.character(f_pad_zero(Station))) # add leading zeros to stations
```

## Convert coordinates from DM to DD
```{r}
chd <- substr(oct$Lat, 3, 3)[1]

# latitude
Lat_split_oct <- str_split_fixed(oct$Lat, chd, 2) %>%
                 as.data.frame()
Lat_split_oct$V2 <- str_remove_all(Lat_split_oct$V2, pattern = "'") %>%
                    as.numeric()
Lat_split_oct$V2 <- Lat_split_oct$V2/60
Lat_split_oct$V1 <- as.numeric(Lat_split_oct$V1)

oct$Lat <- Lat_split_oct$V1 + Lat_split_oct$V2
rm(Lat_split_oct)

# longitude
Long_split_oct <- str_split_fixed(oct$Long, chd, 2) %>%
                  as.data.frame()
Long_split_oct$V2 <- str_remove_all(Long_split_oct$V2, pattern = "'") %>%
                     as.numeric()
Long_split_oct$V2 <- Long_split_oct$V2/60
Long_split_oct$V1 <- as.numeric(Long_split_oct$V1)

oct$Long <- -(Long_split_oct$V1 + Long_split_oct$V2)
rm(Long_split_oct)
rm(chd)
```

## *SKIP SOMETIMES* Fill in missing temp & DO values
```#{r}
# temp
for(i in 1:nrow(oct)) {
  if(oct$Station[i] == "022") {
    cast <- oct$Cast[i]
    oct$Temp[i] <- 0.611 * oct$Temp[oct$Station == "019" & oct$Cast == cast] +
                   0.389 * oct$Temp[oct$Station == "024" & oct$Cast == cast]
  }
  if(oct$Station[i] == "023") {
    cast <- oct$Cast[i]
    oct$Temp[i] <- oct$Temp[oct$Station == "021" & oct$Cast == cast]
  }
  if(oct$Station[i] == "104") {
    cast <- oct$Cast[i]
    oct$Temp[i] <- 0.249 * oct$Temp[oct$Station == "094" & oct$Cast == cast] +
                   0.303 * oct$Temp[oct$Station == "103" & oct$Cast == cast] +
                   0.212 * oct$Temp[oct$Station == "105" & oct$Cast == cast] +
                   0.236 * oct$Temp[oct$Station == "106" & oct$Cast == cast]
  }
}

# DO
for(i in 1:nrow(oct)) {
  if(oct$Station[i] == "022") {
    cast <- oct$Cast[i]
    oct$DO[i] <- 0.611 * oct$DO[oct$Station == "019" & oct$Cast == cast] +
                 0.389 * oct$DO[oct$Station == "024" & oct$Cast == cast]
  }
  if(oct$Station[i] == "023") {
    cast <- oct$Cast[i]
    oct$DO[i] <- oct$DO[oct$Station == "021" & oct$Cast == cast]
  }
  if(oct$Station[i] == "104") {
    cast <- oct$Cast[i]
    oct$DO[i] <- 0.249 * oct$DO[oct$Station == "094" & oct$Cast == cast] +
                 0.303 * oct$DO[oct$Station == "103" & oct$Cast == cast] +
                 0.212 * oct$DO[oct$Station == "105" & oct$Cast == cast] +
                 0.236 * oct$DO[oct$Station == "106" & oct$Cast == cast]
  }
}
```

## Calculate density & carbon system parameters
```{r}
for(i in which(is.na(oct$SeaPressure))) {
  # substitute depth for sites without sea pressure
  oct$SeaPressure[i] <- oct$Depth[i]
  # calculate surface pressure
  oct$Pressure[i] <- oct$SeaPressure[i] + 10.1325
}

# calculate density
oct$Density <- gsw_rho(oct$Salinity, oct$Temp, oct$SeaPressure) # kg/m^3

# apply salinity correction factor to DO
#oct$salF <- exp(-oct$Salinity * (0.017674 - 10.754 / (oct$Temp + 273.15) + 2140.7 / (oct$Temp + 273.15)^2))

#oct$DO_raw <- oct$DO
#oct$DO <- oct$DO * oct$salF

# convert DO from umol/L to umol/kg
oct$DO_L <- oct$DO
oct$DO <- oct$DO / (oct$Density / 1000) # convert m^3 to L

octCarb <- carb(flag = 15,                               # 15 = ALK & DIC given
                var1 = oct$TA[!is.na(oct$Temp)] / 10^6,  # in mol/kg
                var2 = oct$DIC[!is.na(oct$Temp)] / 10^6, # in mol/kg
                S = oct$Salinity[!is.na(oct$Temp)],
                T = oct$Temp[!is.na(oct$Temp)],          # in deg C
                Patm = oct$Pressure[!is.na(oct$Temp)] * 0.098692326671601,
                                                         # in atm
                P = oct$SeaPressure[!is.na(oct$Temp)] / 10,   # in bar
                k1k2 = "l",                              # l = Lueker et al. (2000)
                                                         # kf: unspecified b/c low temps
                ks = "d",                                # d = Dickson (1990)
                b = "l10")                               # l10 = Lee et al. (2010)

# combine oct & carb data
r <- 1
for(i in c(1:38, 40, 42:44, 47:194, 197:228)) {
#for(i in 1:nrow(oct)) {
  oct$pH[i] <- octCarb$pH[r]
  oct$fCO2[i] <- octCarb$fCO2[r]
  oct$pCO2[i] <- octCarb$pCO2[r]
  oct$OmegaAragonite[i] <- octCarb$OmegaAragonite[r]
  oct$OmegaCalcite[i] <- octCarb$OmegaCalcite[r]
  r <- r + 1
}

for(i in 1:nrow(oct)) {
  if(is.na(oct$Temp[i])) {
    oct$pH[i] <- NA
    oct$pCO2[i] <- NA
    oct$OmegaAragonite[i] <- NA
    oct$OmegaCalcite[i] <- NA
  }
}
```

## Calculate AOU
```{r}
# calc absolute sal
oct$AbsSal <- gsw_SA_from_SP(SP = oct$Salinity,
                             p = oct$SeaPressure,
                             longitude = oct$Long,
                             latitude = oct$Lat)

# calc conservative temp
oct$ConsTemp <- gsw_CT_from_t(SA = oct$AbsSal,
                              t = oct$Temp,
                              p = oct$SeaPressure)

# calc O2 sol
oct$O2sol <- gsw_O2sol(SA = oct$AbsSal,
                       CT = oct$ConsTemp,
                       p = oct$SeaPressure,
                       longitude = oct$Long,
                       latitude = oct$Lat)

# calc AOU
oct$AOU <- oct$O2sol - oct$DO
```

# MIXING ANALYSIS

## Find endmember property values & calculate proportional contributions
```{r}
# surface EMs
EM1 <- which(oct$Station == "009" & oct$Cast == "Surface")
  # no longer using 005; isolating NW sites as separate water mass
EM2 <- which(oct$Station == "091" & oct$Cast == "Surface")
EM3 <- which(oct$Station == "043" & oct$Cast == "Surface")

EM7 <- which(oct$Station == "003" & oct$Cast == "Surface")

# bottom EMs
EM4 <- which(oct$Station == "033" & oct$Cast == "Bottom")
EM5 <- which(oct$Station == "021" & oct$Cast == "Bottom")
EM6 <- which(oct$Station == "076" & oct$Cast == "Bottom")

# pull values for EMs
S1 <- oct$Salinity[EM1]
S2 <- oct$Salinity[EM2]
S3 <- oct$Salinity[EM3]
S7 <- oct$Salinity[EM7]

S4 <- oct$Salinity[EM4]
S5 <- oct$Salinity[EM5]
S6 <- oct$Salinity[EM6]

T1 <- oct$Temp[EM1]
T2 <- oct$Temp[EM2]
T3 <- oct$Temp[EM3]
T7 <- oct$Temp[EM7]

T4 <- oct$Temp[EM4]
T5 <- oct$Temp[EM5]
T6 <- oct$Temp[EM6]

DIC1 <- oct$DIC[EM1]
DIC2 <- oct$DIC[EM2]
DIC3 <- oct$DIC[EM3]
DIC7 <- oct$DIC[EM7]

DIC4 <- oct$DIC[EM4]
DIC5 <- oct$DIC[EM5]
DIC6 <- oct$DIC[EM6]

TA1 <- oct$TA[EM1]
TA2 <- oct$TA[EM2]
TA3 <- oct$TA[EM3]
TA7 <- oct$TA[EM7]

TA4 <- oct$TA[EM4]
TA5 <- oct$TA[EM5]
TA6 <- oct$TA[EM6]
```

# Surface: triangle
```{r}
# surface EM1
EMs1 <- oct$Salinity[oct$Cast == "Surface" &
                     !is.na(oct$Temp) &
                     oct$Station > "008" &
                     oct$Salinity >= S1 - 0.15 & oct$Salinity <= S1 + 0.15 &
                     oct$Temp >= T1 - 0.3 & oct$Temp <= T1 + 0.3]
for(i in 1:length(EMs1)) {
  EMs1[i] <- which(oct$Salinity == EMs1[i])
}
for(i in 1:length(EMs1)) {
  print(oct$Station[EMs1[i]])
}

# calc mean & sd for later use
mean_sal_EMs1 <- mean(oct$Salinity[EMs1])
sd_sal_EMs1 <- sd(oct$Salinity[EMs1])
sal_err1 <- sqrt((1/length(EMs1)) * (0.003^2 * length(EMs1)))
err_sal_EMs1 <- sd_sal_EMs1 + sal_err1

mean_temp_EMs1 <- mean(oct$Temp[EMs1])
sd_temp_EMs1 <- sd(oct$Temp[EMs1])
temp_err1 <- sqrt((1/length(EMs1)) * (0.002^2 * length(EMs1)))
err_temp_EMs1 <- sd_temp_EMs1 + temp_err1

# surface EM2
EMs2 <- oct$Salinity[oct$Cast == "Surface" &
                     !is.na(oct$Temp) &
                     oct$Station > "008" &
                     oct$Salinity >= S2 - 0.15 & oct$Salinity <= S2 + 0.15 &
                     oct$Temp >= T2 - 0.3 & oct$Temp <= T2 + 0.3]
for(i in 1:length(EMs2)) {
  EMs2[i] <- which(oct$Salinity == EMs2[i])
}
for(i in 1:length(EMs2)) {
  print(oct$Station[EMs2[i]])
}

# calc mean & sd for later use
mean_sal_EMs2 <- mean(oct$Salinity[EMs2])
sd_sal_EMs2 <- sd(oct$Salinity[EMs2])
sal_err2 <- sqrt((1/length(EMs2)) * (0.003^2 * length(EMs2)))
err_sal_EMs2 <- sd_sal_EMs2 + sal_err2

mean_temp_EMs2 <- mean(oct$Temp[EMs2])
sd_temp_EMs2 <- sd(oct$Temp[EMs2])
temp_err2 <- sqrt((1/length(EMs2)) * (0.002^2 * length(EMs2)))
err_temp_EMs2 <- sd_temp_EMs2 + temp_err2

# surface EM3
EMs3 <- oct$Salinity[oct$Cast == "Surface" &
                     !is.na(oct$Temp) &
                     oct$Station > "008" &
                     oct$Salinity >= S3 - 0.15 & oct$Salinity <= S3 + 0.15 &
                     oct$Temp >= T3 - 0.3 & oct$Temp <= T3 + 0.3]
for(i in 1:length(EMs3)) {
  EMs3[i] <- which(oct$Salinity == EMs3[i])
  EMs3[i+1] <- which(oct$Cast =="Surface" & oct$Station == "113")
}
for(i in 1:length(EMs3)) {
  print(oct$Station[EMs3[i]])
}

# calc mean & sd for later use
mean_sal_EMs3 <- mean(oct$Salinity[EMs3])
sd_sal_EMs3 <- sd(oct$Salinity[EMs3])
sal_err3 <- sqrt((1/length(EMs3)) * (0.003^2 * length(EMs3)))
err_sal_EMs3 <- sd_sal_EMs3 + sal_err3

mean_temp_EMs3 <- mean(oct$Temp[EMs3])
sd_temp_EMs3 <- sd(oct$Temp[EMs3])
temp_err3 <- sqrt((1/length(EMs3)) * (0.002^2 * length(EMs3)))
err_temp_EMs3 <- sd_temp_EMs3 + temp_err3
```

```{r}
summ1 <- read.table("data/mixing/summary_statistics1.txt", skip = 8) %>%
  dplyr::select(-V1) %>%
  separate(V2, into = c("Station", "EM")) %>%
  rename(Mean = V3, SD = V4)

oct$EM1 <- NA
oct$EM1sd <- NA
oct$EM2 <- NA
oct$EM2sd <- NA
oct$EM3 <- NA
oct$EM3sd <- NA
oct$EM4 <- NA
oct$EM4sd <- NA
oct$EM5 <- NA
oct$EM5sd <- NA
oct$EM6 <- NA
oct$EM6sd <- NA
oct$EM7 <- NA
oct$EM7sd <- NA
oct$sum <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface" &
     oct$Station[i] > "008" &
     oct$Station[i] != "022" &
     oct$Station[i] != "023" &
     oct$Station[i] != "104") {
    oct$EM1[i] <- summ1$Mean[summ1$EM == "EM1" &
                           summ1$Station == as.integer(oct$Station[i])]
    oct$EM1sd[i] <- summ1$SD[summ1$EM == "EM1" &
                           summ1$Station == as.integer(oct$Station[i])]
    oct$EM2[i] <- summ1$Mean[summ1$EM == "EM2" &
                           summ1$Station == as.integer(oct$Station[i])]
    oct$EM2sd[i] <- summ1$SD[summ1$EM == "EM2" &
                           summ1$Station == as.integer(oct$Station[i])]
    oct$EM3[i] <- summ1$Mean[summ1$EM == "EM3" &
                           summ1$Station == as.integer(oct$Station[i])]
    oct$EM3sd[i] <- summ1$SD[summ1$EM == "EM3" &
                           summ1$Station == as.integer(oct$Station[i])]
    oct$sum[i] <- sum(oct$EM1[i], oct$EM2[i], oct$EM3[i])
  }
}
```

# Surface: linear
```{r}
# surface EM7
EMs7 <- oct$Salinity[oct$Cast == "Surface" &
                     !is.na(oct$Temp) &
                     oct$Salinity >= S7 - 0.15 & oct$Salinity <= S7 + 0.15 &
                     oct$Temp >= T7 - 0.3 & oct$Temp <= T7 + 0.3]
for(i in 1:length(EMs7)) {
  EMs7[i] <- which(oct$Salinity == EMs7[i])
}
for(i in 1:length(EMs7)) {
  print(oct$Station[EMs7[i]])
}

# calc mean & sd for later use
mean_sal_EMs7 <- mean(oct$Salinity[EMs7])
sd_sal_EMs7 <- sd(oct$Salinity[EMs7])
sal_err2 <- sqrt((1/length(EMs7)) * (0.003^2 * length(EMs7)))
err_sal_EMs7 <- sd_sal_EMs7 + sal_err2

mean_temp_EMs7 <- mean(oct$Temp[EMs7])
sd_temp_EMs7 <- sd(oct$Temp[EMs7])
temp_err2 <- sqrt((1/length(EMs7)) * (0.002^2 * length(EMs7)))
err_temp_EMs7 <- sd_temp_EMs7 + temp_err2
```

```{r}
summ3 <- read.table("data/mixing/summary_statistics3.txt", skip = 8) %>%
  dplyr::select(-V1) %>%
  separate(V2, into = c("Station", "EM")) %>%
  rename(Mean = V3, SD = V4)

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface" &
     oct$Station[i] < "006") {
    oct$EM1[i] <- summ3$Mean[summ3$EM == "EM1" &
                           summ3$Station == as.integer(oct$Station[i])]
    oct$EM1sd[i] <- summ3$SD[summ3$EM == "EM1" &
                           summ3$Station == as.integer(oct$Station[i])]
    oct$EM7[i] <- summ3$Mean[summ3$EM == "EM7" &
                           summ3$Station == as.integer(oct$Station[i])]
    oct$EM7sd[i] <- summ3$SD[summ3$EM == "EM7" &
                           summ3$Station == as.integer(oct$Station[i])]
    oct$sum[i] <- sum(oct$EM1[i], oct$EM7[i])
  }
}
```

# Bottom: triangle
```{r}
# bottom EM4
EMs4 <- oct$Salinity[oct$Cast == "Bottom" &
                     !is.na(oct$Temp) &
                     oct$Salinity >= S4 - 0.25 & oct$Salinity <= S4 + 0.25 &
                     oct$Temp >= T4 - 0.6 & oct$Temp <= T4 + 0.6]
for(i in 1:length(EMs4)) {
  EMs4[i] <- which(oct$Salinity == EMs4[i])
}
for(i in 1:length(EMs4)) {
  print(oct$Station[EMs4[i]])
}

# calc mean & sd for later use
mean_sal_EMs4 <- mean(oct$Salinity[EMs4])
sd_sal_EMs4 <- sd(oct$Salinity[EMs4])
sal_err4 <- sqrt((1/length(EMs4)) * (0.003^2 * length(EMs4)))
err_sal_EMs4 <- sd_sal_EMs4 + sal_err4

mean_temp_EMs4 <- mean(oct$Temp[EMs4])
sd_temp_EMs4 <- sd(oct$Temp[EMs4])
temp_err4 <- sqrt((1/length(EMs4)) * (0.002^2 * length(EMs4)))
err_temp_EMs4 <- sd_temp_EMs4 + temp_err4

# bottom EM5
EMs5 <- oct$Salinity[oct$Cast == "Bottom" &
                     !is.na(oct$Temp) &
                     oct$Salinity >= S5 - 0.25 & oct$Salinity <= S5 + 0.25 &
                     oct$Temp >= T5 - 0.6 & oct$Temp <= T5 + 0.6]
for(i in 1:length(EMs5)) {
  EMs5[i] <- which(oct$Salinity == EMs5[i])
}
for(i in 1:length(EMs5)) {
  print(oct$Station[EMs5[i]])
}

# calc mean & sd for later use
mean_sal_EMs5 <- mean(oct$Salinity[EMs5])
sd_sal_EMs5 <- sd(oct$Salinity[EMs5])
sal_err5 <- sqrt((1/length(EMs5)) * (0.003^2 * length(EMs5)))
err_sal_EMs5 <- sd_sal_EMs5 + sal_err5

mean_temp_EMs5 <- mean(oct$Temp[EMs5])
sd_temp_EMs5 <- sd(oct$Temp[EMs5])
temp_err5 <- sqrt((1/length(EMs5)) * (0.002^2 * length(EMs5)))
err_temp_EMs5 <- sd_temp_EMs5 + temp_err5

# bottom EM6
EMs6 <- oct$Salinity[oct$Cast == "Bottom" &
                     !is.na(oct$Temp) &
                     oct$Salinity >= S6 - 0.25 & oct$Salinity <= S6 + 0.25 &
                     oct$Temp >= T6 - 0.6 & oct$Temp <= T6 + 0.6]
for(i in 1:length(EMs6)) {
  EMs6[i] <- which(oct$Salinity == EMs6[i])
}
for(i in 1:length(EMs6)) {
  print(oct$Station[EMs6[i]])
}

# calc mean & sd for later use
mean_sal_EMs6 <- mean(oct$Salinity[EMs6])
sd_sal_EMs6 <- sd(oct$Salinity[EMs6])
sal_err6 <- sqrt((1/length(EMs6)) * (0.003^2 * length(EMs6)))
err_sal_EMs6 <- sd_sal_EMs6 + sal_err6

mean_temp_EMs6 <- mean(oct$Temp[EMs6])
sd_temp_EMs6 <- sd(oct$Temp[EMs6])
temp_err6 <- sqrt((1/length(EMs6)) * (0.002^2 * length(EMs6)))
err_temp_EMs6 <- sd_temp_EMs6 + temp_err6
```

```{r}
summ2 <- read.table("data/mixing/summary_statistics2.txt", skip = 8) %>%
  dplyr::select(-V1) %>%
  separate(V2, into = c("Station", "EM")) %>%
  rename(Mean = V3, SD = V4)

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Bottom" &
     oct$Station[i] != "022" &
     oct$Station[i] != "023" &
     oct$Station[i] != "104") {
    oct$EM4[i] <- summ2$Mean[summ2$EM == "EM4" &
                           summ2$Station == as.integer(oct$Station[i])]
    oct$EM4sd[i] <- summ2$SD[summ2$EM == "EM4" &
                           summ2$Station == as.integer(oct$Station[i])]
    oct$EM5[i] <- summ2$Mean[summ2$EM == "EM5" &
                           summ2$Station == as.integer(oct$Station[i])]
    oct$EM5sd[i] <- summ2$SD[summ2$EM == "EM5" &
                           summ2$Station == as.integer(oct$Station[i])]
    oct$EM6[i] <- summ2$Mean[summ2$EM == "EM6" &
                           summ2$Station == as.integer(oct$Station[i])]
    oct$EM6sd[i] <- summ2$SD[summ2$EM == "EM6" &
                           summ2$Station == as.integer(oct$Station[i])]
    oct$sum[i] <- sum(oct$EM4[i], oct$EM5[i], oct$EM6[i])
  }
}
```

## Calculate mixing-normalized DIC, TA & DO values
```{r}
DIC1 <- mean(oct$DIC[EMs1])
DIC2 <- mean(oct$DIC[EMs2])
DIC3 <- mean(oct$DIC[EMs3])
DIC4 <- mean(oct$DIC[EMs4])
DIC5 <- mean(oct$DIC[EMs5])
DIC6 <- mean(oct$DIC[EMs6])
DIC7 <- mean(oct$DIC[EMs7])

sdDIC1 <- sd(oct$DIC[EMs1])
sdDIC2 <- sd(oct$DIC[EMs2])
sdDIC3 <- sd(oct$DIC[EMs3])
sdDIC4 <- sd(oct$DIC[EMs4])
sdDIC5 <- sd(oct$DIC[EMs5])
sdDIC6 <- sd(oct$DIC[EMs6])
sdDIC7 <- sd(oct$DIC[EMs7])

TA1 <- mean(oct$TA[EMs1])
TA2 <- mean(oct$TA[EMs2])
TA3 <- mean(oct$TA[EMs3])
TA4 <- mean(oct$TA[EMs4])
TA5 <- mean(oct$TA[EMs5])
TA6 <- mean(oct$TA[EMs6])
TA7 <- mean(oct$TA[EMs7])

sdTA1 <- sd(oct$TA[EMs1])
sdTA2 <- sd(oct$TA[EMs2])
sdTA3 <- sd(oct$TA[EMs3])
sdTA4 <- sd(oct$TA[EMs4])
sdTA5 <- sd(oct$TA[EMs5])
sdTA6 <- sd(oct$TA[EMs6])
sdTA7 <- sd(oct$TA[EMs7])

DO1 <- mean(oct$DO[EMs1])
DO2 <- mean(oct$DO[EMs2])
DO3 <- mean(oct$DO[EMs3])
DO4 <- mean(oct$DO[EMs4])
DO5 <- mean(oct$DO[EMs5])
DO6 <- mean(oct$DO[EMs6])
DO7 <- mean(oct$DO[EMs7])

sdDO1 <- sd(oct$DO[EMs1])
sdDO2 <- sd(oct$DO[EMs2])
sdDO3 <- sd(oct$DO[EMs3])
sdDO4 <- sd(oct$DO[EMs4])
sdDO5 <- sd(oct$DO[EMs5])
sdDO6 <- sd(oct$DO[EMs6])
sdDO7 <- sd(oct$DO[EMs7])

oct$DICn <- NA
oct$dDIC <- NA
oct$TAn <- NA
oct$dTA <- NA
oct$DOn <- NA
oct$dDO <- NA

## process used to solve the system of eq is at the end of this script

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface" &
     oct$Station[i] > "005") {
       oct$DICn[i] = oct$EM1[i]*DIC1 + oct$EM2[i]*DIC2 + oct$EM3[i]*DIC3
       oct$dDIC[i] = oct$DIC[i] - oct$DICn[i]   # observed - expected
       oct$TAn[i] = oct$EM1[i]*TA1 + oct$EM2[i]*TA2 + oct$EM3[i]*TA3
       oct$dTA[i] = oct$TA[i] - oct$TAn[i]   # observed - expected
       oct$DOn[i] = oct$EM1[i]*DO1 + oct$EM2[i]*DO2 + oct$EM3[i]*DO3
       oct$dDO[i] = oct$DO[i] - oct$DOn[i]   # observed - expected
       oct$sdDICn[i] = sqrt(oct$EM1sd[i]^2 * DIC1 + sdDIC1^2 * oct$EM1[i] +
                            oct$EM2sd[i]^2 * DIC2 + sdDIC2^2 * oct$EM2[i] +
                            oct$EM3sd[i]^2 * DIC3 + sdDIC3^2 * oct$EM3[i])
       oct$sdTAn[i] = sqrt(oct$EM1sd[i]^2 * TA1 + sdTA1^2 * oct$EM1[i] +
                           oct$EM2sd[i]^2 * TA2 + sdTA2^2 * oct$EM2[i] +
                           oct$EM3sd[i]^2 * TA3 + sdTA3^2 * oct$EM3[i])
       oct$sdDOn[i] = sqrt(oct$EM1sd[i]^2 * DO1 + sdDO1^2 * oct$EM1[i] +
                           oct$EM2sd[i]^2 * DO2 + sdDO2^2 * oct$EM2[i] +
                           oct$EM3sd[i]^2 * DO3 + sdDO3^2 * oct$EM3[i])
     } else if(oct$Cast[i] == "Bottom") {
       oct$DICn[i] = oct$EM4[i]*DIC4 + oct$EM5[i]*DIC5 + oct$EM6[i]*DIC6
       oct$dDIC[i] = oct$DIC[i] - oct$DICn[i]   # observed - expected
       oct$TAn[i] = oct$EM4[i]*TA4 + oct$EM5[i]*TA5 + oct$EM6[i]*TA6
       oct$dTA[i] = oct$TA[i] - oct$TAn[i]   # observed - expected
       oct$DOn[i] = oct$EM4[i]*DO4 + oct$EM5[i]*DO5 + oct$EM6[i]*DO6
       oct$dDO[i] = oct$DO[i] - oct$DOn[i]   # observed - expected
       oct$sdDICn[i] = sqrt(oct$EM4sd[i]^2 * DIC4 + sdDIC4^2 * oct$EM4[i] +
                            oct$EM5sd[i]^2 * DIC5 + sdDIC5^2 * oct$EM5[i] +
                            oct$EM6sd[i]^2 * DIC6 + sdDIC6^2 * oct$EM6[i])
       oct$sdTAn[i] = sqrt(oct$EM4sd[i]^2 * TA4 + sdTA4^2 * oct$EM4[i] +
                           oct$EM5sd[i]^2 * TA5 + sdTA5^2 * oct$EM5[i] +
                           oct$EM6sd[i]^2 * TA6 + sdTA6^2 * oct$EM6[i])
       oct$sdDOn[i] = sqrt(oct$EM4sd[i]^2 * DO4 + sdDO4^2 * oct$EM4[i] +
                           oct$EM5sd[i]^2 * DO5 + sdDO5^2 * oct$EM5[i] +
                           oct$EM6sd[i]^2 * DO6 + sdDO6^2 * oct$EM6[i])
     } else {
       oct$DICn[i] = oct$EM1[i]*DIC1 + oct$EM7[i]*DIC7
       oct$dDIC[i] = oct$DIC[i] - oct$DICn[i]   # observed - expected
       oct$TAn[i] = oct$EM1[i]*TA1 + oct$EM7[i]*TA7
       oct$dTA[i] = oct$TA[i] - oct$TAn[i]   # observed - expected
       oct$DOn[i] = oct$EM1[i]*DO1 + oct$EM7[i]*DO7
       oct$dDO[i] = oct$DO[i] - oct$DOn[i]   # observed - expected
       oct$sdDICn[i] = sqrt(oct$EM1sd[i]^2 * DIC1 + sdDIC1^2 * oct$EM1[i] +
                            oct$EM7sd[i]^2 * DIC7 + sdDIC7^2 * oct$EM7[i])
       oct$sdTAn[i] = sqrt(oct$EM1sd[i]^2 * TA1 + sdTA1^2 * oct$EM1[i] +
                           oct$EM7sd[i]^2 * TA7 + sdTA7^2 * oct$EM7[i])
       oct$sdDOn[i] = sqrt(oct$EM1sd[i]^2 * DO1 + sdDO1^2 * oct$EM1[i] +
                           oct$EM7sd[i]^2 * DO7 + sdDO7^2 * oct$EM7[i])
     }
}
```

## Calculate air-sea CO2 flux
### Schmidt number
```{r}
# F = k*K0(pCO2w – pCO2a)       # F: mass/area*time
                                # k: length/time
                                # K0: mass/volume*pressure (solubility)

# Schmidt number: kinematic viscosity of the water divided by diffusion coefficient of the gas
  # gas- & temp-specific; also somewhat dependent on salinity

  # Sc = A + Bt + Ct^2 + Dt^3 + Et^4
    # t in °C
    # kinematic viscosity from Sharqawy et al. 2010
    # diffusion coefficient from Jähne et al. 1987

A = 2116.8
B = -136.25
C = 4.7353
D = -0.092307
E = 0.000755566

oct$Sc <- NA

# library(marelac)

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    t = oct$Temp[i]
    oct$Sc[i] = A + B*t + C*t^2 + D*t^3 + E*t^4
    # Schmidt number check
    # oct$Sc2[i] <- gas_schmidt(t, species = "CO2") # calculated @ sal = 35
  }
}

# which(abs(oct$Sc - oct$Sc2) > 7) # all w/in 7 of each other
```

### Gas transfer velocity pt. 1: wind speeds
```{r}
# sample collection: Oct 5-10, 2021 GMT
# 63-day period centered on Oct 7, 2021
# Sep 6 - Nov 7

# first satellite
satA <- nc_open("./data/winds/KNMI-GLO-WIND_L3-OBS_METOP-A_ASCAT_25_ASC_V2_oct.nc")

lon <- ncvar_get(satA, "lon")
lat <- ncvar_get(satA, "lat")
time <- ncvar_get(satA, "time")
t.units <- ncatt_get(satA, "time", "units")

# convert time
#t.units$value   # "seconds since 1990-01-01 00:00:00"
# chron() calculates *days* since origin
#chron(time/60/60/24, origin = c(month = 1, day = 1, year = 1990))

wind_array <- ncvar_get(satA, "wind_speed")
fillvalue <- ncatt_get(satA, "wind_speed", "_FillValue")
wind_array[wind_array == fillvalue$value] <- NA

wind_6day <- wind_array[ , , 30:35] # 6-day period Oct 5-10
#image(lon, lat, wind_slice, col = mako(40, direction = -1))

wind_df_A <- data.frame(matrix(ncol = 4, nrow = 0))

# fill dataframe
for(i in 1:6) {
  lonlat <- as.matrix(expand.grid(lon, lat))
  wind_slice <- wind_6day[ , , i]
  wind_vec <- as.vector(wind_slice)
  day_vec <- rep(i, length(wind_vec))
  wind_df_A <- rbind(wind_df_A, data.frame(cbind(day_vec, lonlat, wind_vec)))
}
names(wind_df_A) <- c("day", "lon", "lat", "wind_speed")

# second satellite
satB <- nc_open("./data/winds/KNMI-GLO-WIND_L3-OBS_METOP-B_ASCAT_25_ASC_V2_oct.nc")

lon <- ncvar_get(satB, "lon")
lat <- ncvar_get(satB, "lat")
time <- ncvar_get(satB, "time")

#chron(time/60/60/24, origin = c(month = 1, day = 1, year = 1990))

wind_array <- ncvar_get(satB, "wind_speed")
fillvalue <- ncatt_get(satB, "wind_speed", "_FillValue")
wind_array[wind_array == fillvalue$value] <- NA

wind_6day <- wind_array[ , , 30:35]
#image(lon, lat, wind_slice, col = mako(40, direction = -1))

wind_df_B <- data.frame(matrix(ncol = 4, nrow = 0))

# fill dataframe
for(i in 1:6) {
  lonlat <- as.matrix(expand.grid(lon, lat))
  wind_slice <- wind_6day[ , , i]
  wind_vec <- as.vector(wind_slice)
  day_vec <- rep(i, length(wind_vec))
  wind_df_B <- rbind(wind_df_B, data.frame(cbind(day_vec, lonlat, wind_vec)))
}
names(wind_df_B) <- c("day", "lon", "lat", "wind_speed")

# third satellite
satC <- nc_open("./data/winds/KNMI-GLO-WIND_L3-OBS_METOP-C_ASCAT_25_ASC_V2_oct.nc")

lon <- ncvar_get(satC, "lon")
lat <- ncvar_get(satC, "lat")
time <- ncvar_get(satC, "time")

#chron(time/60/60/24, origin = c(month = 1, day = 1, year = 1990))

wind_array <- ncvar_get(satC, "wind_speed")
fillvalue <- ncatt_get(satC, "wind_speed", "_FillValue")
wind_array[wind_array == fillvalue$value] <- NA

wind_6day <- wind_array[ , , 30:35]
#image(lon, lat, wind_slice, col = mako(40, direction = -1))

wind_df_C <- data.frame(matrix(ncol = 4, nrow = 0))

# fill dataframe
for(i in 1:6) {
  lonlat <- as.matrix(expand.grid(lon, lat))
  wind_slice <- wind_6day[ , , i]
  wind_vec <- as.vector(wind_slice)
  day_vec <- rep(i, length(wind_vec))
  wind_df_C <- rbind(wind_df_C, data.frame(cbind(day_vec, lonlat, wind_vec)))
}
names(wind_df_C) <- c("day", "lon", "lat", "wind_speed")

# merge dataframes
wind_df <- bind_rows(wind_df_A, wind_df_B, wind_df_C) %>%
  mutate(lon = lon - 360) %>%
  filter(lon >= -70.5 & lon <= -66) %>%
  filter(lat >= 40 & lat <= 42.5) %>%
  group_by(lon, lat) %>%
  summarise(mean_wind = mean(wind_speed, na.rm = TRUE)) %>%
  mutate(mean_wind = ifelse(is.nan(mean_wind), NA, mean_wind)) %>%
  na.omit()

#ggplot(wind_df) +
#  geom_point(aes(x = lon, y = lat, col = mean_wind), size = 15, shape = 15) +
#  scale_color_viridis(limits = c(0.6, 12.4), breaks = c(2, 4, 6, 8, 10),
#                      name = "wspd") +
#  geom_point(data = oct, aes(x = Long, y = Lat), shape = 18, size = 4) +
#  xlim(-70.5, -66) +
#  ylim(40, 42.5) +
#  theme_bw() +
#  theme(axis.title = element_blank())

oct$wspd <- NA

# assign wind speed to each station
for(i in 1:nrow(oct)) {
  oct$wspd[i] = mean(wind_df$mean_wind[which(abs(oct$Lat[i] - wind_df$lat) +
                                           abs(oct$Long[i] - wind_df$lon) ==
                                       min(abs(oct$Lat[i] - wind_df$lat) +
                                           abs(oct$Long[i] - wind_df$lon)))])
}
```

### Gas transfer velocity pt. 2
```{r}
# k (cm/hr) = 0.251 * U10^2 * (Sc/660)^-0.5   (Wanninkhof 2014)
  # U10 (m/s) = average of neutral stability winds at 10-m height
      # ****need data corr. to 10m****
      # average 30 days around cruise
# k (cm/hr) = 0.266 * U10^2 * (Sc/600)^-0.5   (Ho et al. 2006)

oct$k <- NA   # gas transfer velocity (cm/hr)

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    # Wanninkhof 2014
    oct$k[i] = 0.251 * oct$wspd[i]^2 * (oct$Sc[i]/660)^-0.5
    # Ho et al. 2006
    #oct$k2[i] = 0.266 * oct$wspd[i]^2 * (oct$Sc[i]/600)^-0.5
  }
}

# which(abs(oct$k - oct$k2) > 0.11) # all w/in 0.11 of each other
```

### Solubility constant & flux calc
```{r}
# ln(beta) = Α1 + Α2(100/Τ) + A3ln(T/100) + S[(B1 + B2(T/100) + B3(T/100)^2]
  # beta = K' (mol/L*atm) from Weiss 1974
  # T in K
  # S in ppt (PSU)

A1 = -58.0931
A2 = 90.5069
A3 = 22.2940
B1 = 0.027766
B2 = -0.025888
B3 = 0.0050578

oct$K.prime <- NA
oct$pH2O <- NA   # seawater vapor pressure

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    T = oct$Temp[i] + 273.15
    S = oct$Salinity[i]
    oct$K.prime[i] = exp(A1 + A2*(100/T) + A3*log(T/100) + S*(B1 + B2*(T/100) + B3*(T/100)^2))
    # partial pressure of H2O right above the sea surface
    oct$pH2O[i] = vapress(oct$Salinity[i], oct$Temp[i], form = "d2007")   # atm
  }
}

# K' ≈ K0 * f/(X(P – PH2O))
  # K' in mol/L*atm
  # f: fugacity
  # X: mole fraction (dry)
  # P: total pressure
  # pH2O: seawater vapor pressure

## OOI data
pCO2_data <- read.csv("./data/pCO2/OctCruiseCNSM.csv") %>%
  filter(DateTime >= "05-Oct-2021")

P <- mean(pCO2_data$gas_stream_pressure) / 1013.25   # hPa to atm
oct$K0 <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    xCO2 = p2xCO2(oct$Salinity[i], oct$Temp[i], Patm = P, oct$pCO2[i])   # ppm
    oct$K0[i] = oct$K.prime[i] * xCO2 * (P - oct$pH2O[i]) / oct$fCO2[i]
  }
}

# F = k*K0(pCO2w – pCO2a)

pCO2a <- mean(pCO2_data$partial_pressure_co2_atm)

oct$flux <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    k = oct$k[i] / 100 * 24         # cm/hr --> m/d
    K0 = oct$K0[i] * 10^6 * 10^3 / 10^6    # mol/(L*atm) --> umol/(m^3*uatm)
    diff.pCO2 = oct$pCO2[i] - pCO2a    # uatm
    oct$flux[i] = k * K0 * diff.pCO2   # umol/(m^2*d)
  }
}
```

## Add mixed-layer depths
```{r}
MLD <- read.csv("./data/CTD/oct_MLD.csv")

oct$MLD <- NA
oct$MLD_frac <- NA

for(i in 1:nrow(oct)) {
  if(oct$Station[i] != "022" &
     oct$Station[i] != "023" &
     oct$Station[i] != "104") {
    oct$MLD[i] = MLD$MLD[MLD$Station == as.integer(oct$Station[i])]
    depth = oct$Depth[oct$Station == oct$Station[i] &
                      oct$Cast == "Bottom"]
    oct$MLD_frac[i] <- oct$MLD[i] / depth
  }
}
```

## Add air-sea flux for fully mixed sites
```{r}
for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Bottom" &
     !is.na(oct$MLD_frac[i]) &
     oct$MLD_frac[i] > 0.9) {
    oct$flux[i] = oct$flux[which(oct$Cast == "Surface" &
                                 oct$Station == oct$Station[i])]
  }
}
```

## Load residence time data
```{r}
resTimes <- read.csv("data/GB_ResTimes.csv")

LongW <- rep(NA, 160)
LongE <- rep(NA, 160)
LatN <- rep(NA, 160)
LatS <- rep(NA, 160)
ResTime <- rep(NA, 160)

res.new <- as.data.frame(cbind(LongW, LongE, LatN, LatS, ResTime))

for(i in 1:nrow(resTimes)) {
  longW <- resTimes$LongW[i]
  longE <- resTimes$LongE[i]
  latN <- resTimes$LatN[i]
  latS <- resTimes$LatS[i]
  res.new$LongW[i*4-3] <- longW
  res.new$LongE[i*4-3] <- longE - 0.25
  res.new$LatN[i*4-3] <- latN
  res.new$LatS[i*4-3] <- latS + 0.25
  res.new$LongW[i*4-2] <- longW + 0.25
  res.new$LongE[i*4-2] <- longE
  res.new$LatN[i*4-2] <- latN
  res.new$LatS[i*4-2] <- latS + 0.25
  res.new$LongW[i*4-1] <- longW
  res.new$LongE[i*4-1] <- longE - 0.25
  res.new$LatN[i*4-1] <- latN - 0.25
  res.new$LatS[i*4-1] <- latS
  res.new$LongW[i*4] <- longW + 0.25
  res.new$LongE[i*4] <- longE
  res.new$LatN[i*4] <- latN - 0.25
  res.new$LatS[i*4] <- latS
  res.new$ResTime[(i*4-3):(i*4)] <- resTimes$ResTime[i] / 4
}

#ggplot(resTimes, aes(x = LongW, y = LatN, col = ResTime)) +
#  geom_point(shape = 15, size = 12) +
#  scale_color_viridis() +
#  theme_bw()

#ggplot(res.new, aes(x = LongW, y = LatN, col = ResTime)) +
#  geom_point(shape = 15, size = 8) +
#  scale_color_viridis() +
#  theme_bw()

#ggplot(res.new, aes(x = LongE, y = LatS, col = ResTime)) +
#  geom_point(shape = 15, size = 8) +
#  scale_color_viridis() +
#  theme_bw()

# assign res time to each station
for(i in 1:nrow(oct)) {
  oct$resTime[i] = res.new$ResTime[which(oct$Lat[i] < res.new$LatN &
                                           oct$Lat[i] >= res.new$LatS &
                                           oct$Long[i] > res.new$LongW &
                                           oct$Long[i] <= res.new$LongE)]
}
```

## Calculate DICair-sea
```{r}
# umol/(m^2*d) * 1/[MLD]m * m^3/[rho]kg * [res.time]days = umol/kg

oct$DICf <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface" &
     !is.na(oct$MLD_frac[i])) {
      oct$DICf[i] = -1 * oct$flux[i] / oct$MLD[i] / oct$Density[i] * oct$resTime[i]
  }
}

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Bottom" &
     !is.na(oct$MLD_frac[i]) &
     oct$MLD_frac[i] > 0.9) {
    oct$DICf[i] = oct$DICf[which(oct$Cast == "Surface" &
                                 oct$Station == oct$Station[i])]
  }
}
```

## Calculate air-sea O2 flux
```{r}
# Schmidt number (Wilke & Chang 1955, as adapted by Hayduk & Laudie 1974)
A = 1920.4
B = -135.6
C = 5.2122
D = -0.10939
E = 0.00093777

oct$Sc.O2 <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    t = oct$Temp[i]
    oct$Sc.O2[i] = A + B*t + C*t^2 + D*t^3 + E*t^4
  }
}

# gas transfer velocity
oct$k.O2 <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    oct$k.O2[i] = 0.251 * oct$wspd[i]^2 * (oct$Sc.O2[i]/660)^-0.5
  }
}

# oct$O2sol = O2 sol in umol/kg
oct$O2sol_L <- oct$O2sol * (oct$Density / 1000)

oct$flux.O2 <- NA

# flux
for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    k = oct$k.O2[i] / 100 * 24         # cm/hr --> m/d
    diff.O2 = (oct$DO_L[i] - oct$O2sol_L[i]) * 10^3   # umol/L --> umol/m^3
    oct$flux.O2[i] = k * diff.O2   # umol/(m^2*d)
  }
}

# add to bottom at fully mixed sites
for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Bottom" &
     !is.na(oct$MLD_frac[i]) &
     oct$MLD_frac[i] > 0.9) {
    oct$flux.O2[i] = oct$flux.O2[which(oct$Cast == "Surface" &
                                 oct$Station == oct$Station[i])]
  }
}
```

## Calculate contribution to O2 from flux
```{r}
# umol/(m^2*d) * 1/[MLD]m * m^3/[rho]kg * [res.time]days = umol/kg
oct$DOf <- NA

for(i in 1:nrow(oct)) {
  if(!is.na(oct$MLD_frac[i]) &
     (oct$Cast[i] == "Surface" |
     (oct$Cast[i] == "Bottom" &
     oct$MLD_frac[i] > 0.9))) {
     oct$DOf[i] = -1 * oct$flux.O2[i] / oct$MLD[i] / oct$Density[i] * oct$resTime[i]
  }
}

# add zeros to flux-absent sites for use in calcs
for(i in 1:nrow(oct)) {
  if(is.na(oct$DOf[i])) {
    oct$DOf[i] = 0
  }
}
```

## Convert dDO to DIC & TA signals
```{r}
# subtracting O2 flux at surface & fully mixed sites
oct$DOpr <- oct$dDO - oct$DOf

# calling the "other" component of DO negligible; therefore remaining DO is all aerobic

# dDO umol/kg * 106 (DIC) / 138 (O2) = prod/resp DIC signal
oct$DICpr <- oct$DOpr * -106 / 138

# dDO umol/kg * 17 (TA) / 138 (O2) = prod/resp TA signal
oct$TApr <- oct$DOpr * 17 / 138
```

## Calculate "other" components of DIC & TA
```{r}
# add zeros to flux-absent sites
for(i in 1:nrow(oct)) {
  if(is.na(oct$DICf[i])) {
    oct$DICf[i] <- 0
  }
}

oct$DIC.other <- NA
oct$TA.other <- NA

oct$DIC.other <- oct$DIC - oct$DICn - oct$DICpr - oct$DICf
oct$TA.other = oct$TA - oct$TAn - oct$TApr
```






## Calculate relative contributions from each
```{r}
for(i in 1:nrow(oct)) {
  oct$magnitude[i] <- sum(abs(oct$DICpr[i]), abs(oct$DICf[i]),
                          abs(oct$DIC.other[i]))
  oct$rel.DICpr[i] <- abs(oct$DICpr[i]) / oct$magnitude[i]
  oct$rel.DICf[i] <- abs(oct$DICf[i]) / oct$magnitude[i]
  oct$rel.DICres[i] <- abs(oct$DIC.other[i]) / oct$magnitude[i]
  # check sums
  #oct$rel.sum[i] <- sum(oct$rel.DICpr[i], oct$rel.DICf[i], oct$rel.DICres[i])
  oct$magnitudeT[i] <- sum(abs(oct$TApr[i]), abs(oct$TA.other[i]))
  oct$rel.TApr[i] <- abs(oct$TApr[i]) / oct$magnitudeT[i]
  oct$rel.TAres[i] <- abs(oct$TA.other[i]) / oct$magnitudeT[i]
  # check sums
  #oct$rel.sum[i] <- sum(oct$rel.TApr[i], oct$rel.TAres[i])
}
```









# Surface: triangle

## Bayesian mixing model
```{r}
# create mixture data: surface data w/ NAs & non-triangle sites excluded
read.csv("./data/OctCruiseData.csv") %>%
  rename(Temp = Temperature) %>%
  filter(Filtered == "",
         Cast == "Surface",
         !is.na(Temp),
         Station > 8) %>% # exclude sites 001-008
  select(-Filtered) %>%
  write_csv("./mixing/OctCruiseData_surface.csv")

# load mixture data
mix <- load_mix_data(filename = "./mixing/OctCruiseData_surface.csv", 
                     iso_names = c("Salinity", "Temp"),
                     factors = "Station",
                     fac_random = FALSE, # indiv. station is fixed effect
                     fac_nested = NULL,
                     cont_effects = NULL)

# create source data
EM <- c("EM1", "EM2", "EM3")
MeanTemp <- c(mean_temp_EMs1, mean_temp_EMs2, mean_temp_EMs3)
SDTemp <- c(err_temp_EMs1, err_temp_EMs2, err_temp_EMs3)
MeanSalinity <- c(mean_sal_EMs1, mean_sal_EMs2, mean_sal_EMs3)
SDSalinity <- c(err_sal_EMs1, err_sal_EMs2, err_sal_EMs3)
n <- c(length(EMs1), length(EMs2), length(EMs3))

write.csv(cbind(EM, MeanTemp, SDTemp,
                MeanSalinity, SDSalinity, n), "./mixing/sources_surface.csv",
          row.names = FALSE)

# load source data
source <- load_source_data(filename = "./mixing/sources_surface.csv",
                           source_factors = NULL, 
                           conc_dep = FALSE, 
                           data_type = "means", 
                           mix)

# create discrimination data: 0 because conservative parameters
MeanTemp <- rep(0, 3)
SDTemp <- rep(0, 3)
MeanSalinity <- rep(0, 3)
SDSalinity <- rep(0, 3)

write.csv(cbind(EM, MeanTemp, SDTemp,
                MeanSalinity, SDSalinity), "./mixing/discr_surface.csv",
          row.names = FALSE)

# load discrimination data
discr <- load_discr_data(filename = "./mixing/discr_surface.csv", mix)
```

## Make isospace plot & choose prior
```{r}
iso <- plot_data(filename = "isospace_plot", plot_save_pdf = FALSE,
                 plot_save_png = FALSE, mix, source, discr, return_obj = TRUE)
iso + theme(legend.position = "none")

#iso$plot_env$source.labels$label

calc_area(source = source, mix = mix, discr = discr) # 100.2011

# uninformative (technically "generalist") prior (alpha = 1)
# Dirichlet distribution: all sources treated independently but must sum to 1 (Gelman et al. 2003)
plot_prior(alpha.prior = 1, source, plot_save_pdf = FALSE, plot_save_png = TRUE)
```

## Write model
```{r}
model_filename <- "./surface_model_2.txt"
resid_err <- FALSE # because n=1 per Station
process_err <- TRUE
write_JAGS_model(model_filename, resid_err, process_err, mix, source)

run <- list(chainLength = 3000000, burn = 1500000, thin = 500, chains = 3,
            calcDIC = TRUE)
jags.1.1 <- run_model(run, mix, source, discr, model_filename, alpha.prior = 1)
```

## Check for convergence
```{r}
output_options1 <- list(summary_save = TRUE,
                       summary_name = "summary_statistics1",
                       sup_post = TRUE,
                       plot_post_save_pdf = FALSE,
                       plot_post_name = "posterior_density1",
                       sup_pairs = TRUE,
                       plot_pairs_save_pdf = FALSE,
                       plot_pairs_name = "pairs_plot1",
                       sup_xy = FALSE,
                       plot_xy_save_pdf = FALSE,
                       plot_xy_name = "xy_plot1",
                       gelman = TRUE,
                       heidel = FALSE,
                       geweke = TRUE,
                       diag_save = TRUE,
                       diag_name = "diagnostics1",
                       indiv_effect = FALSE,
                       plot_post_save_png = FALSE,
                       plot_pairs_save_png = FALSE,
                       plot_xy_save_png = FALSE,
                       diag_save_ggmcmc = FALSE,
                       return_obj = TRUE)

options(max.print = 3000) # change global option
output_JAGS(jags.1, mix, source, output_options1)

diag <- output_diagnostics(jags.1.1, mix, source, output_options1)
df.stats <- output_stats(jags.1.1, mix, source, output_options1)
g.post <- output_posteriors(jags.1.1, mix, source, output_options1)

g.post$fac1[[33]]

# Gelman diagnostic should be < 1.05
# w/ "normal" MCMC parameters:                                     31; 0; 0
# w/ "long" MCMC params:                                           16; 0; 0
# w/ run = list(chainLength = 1000000, burn =  200000, thin = 100): 0; 0; 0
# w/ run = list(chainLength = 1000000, burn =  500000, thin = 100): 0; 0; 0
# w/ "very long" MCMC params:
#          list(chainLength = 1000000, burn =  500000, thin = 500): 2; 0; 0
# w/ run = list(chainLength = 2000000, burn =  500000, thin = 500): 0; 0; 0
# w/ "extreme" MCMC params:
#          list(chainLength = 3000000, burn = 1500000, thin = 500): 0; 0; 0

# Geweke diagnostic should have ~5% outside +/-1.96 (~31-32/634) in each chain
# w/ "normal" MCMC parameters:                                       91 / 32 / 62
# w/ "long" MCMC params:                                             36 / 70 / 87
# w/ run = list(chainLength = 1000000, burn =  200000, thin = 100):  90 / 46 / 102
# w/ run = list(chainLength = 1000000, burn =  500000, thin = 100): 116 / 86 / 43
# w/ "very long" MCMC params:
#          list(chainLength = 1000000, burn =  500000, thin = 500):  37 / 32 / 34
# w/ run = list(chainLength = 2000000, burn =  500000, thin = 500):  38 / 38 / 20
# w/ "extreme" MCMC params:
#          list(chainLength = 3000000, burn = 1500000, thin = 500):  22 / 24 / 38
```

## Plots for 1
```{r}
ggplot(oct[oct$Cast == "Surface", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM1)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()

ggplot(oct[oct$Cast == "Surface", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM2)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()

ggplot(oct[oct$Cast == "Surface", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM3)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()



ggplot(oct[oct$Cast == "Surface", ]) +
  #geom_point(aes(x = a1, y = EM1)) +
  geom_text(aes(x = a1, y = EM1, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()

ggplot(oct[oct$Cast == "Surface", ]) +
  #geom_point(aes(x = a2, y = EM2)) +
  geom_text(aes(x = a2, y = EM2, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()

ggplot(oct[oct$Cast == "Surface", ]) +
  #geom_point(aes(x = a3, y = EM3)) +
  geom_text(aes(x = a3, y = EM3, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()
```

# Surface: linear

## Bayesian mixing model
```{r}
# create mixture data: nearshore data (001 - 005)
read.csv("./data/OctCruiseData.csv") %>%
  rename(Temp = Temperature) %>%
  filter(Filtered == "",
         Cast == "Surface",
         Station < 6) %>%
  select(-Filtered) %>%
  write_csv("./mixing/OctCruiseData_linear.csv")

# load mixture data
mix <- load_mix_data(filename = "./mixing/OctCruiseData_linear.csv", 
                     iso_names = c("Salinity", "Temp"),
                     factors = "Station",
                     fac_random = FALSE, # indiv. station is fixed effect
                     fac_nested = NULL,
                     cont_effects = NULL)

# create source data
EM <- c("EM1", "EM7")
MeanTemp <- c(mean_temp_EMs1, mean_temp_EMs7)
SDTemp <- c(err_temp_EMs1, err_temp_EMs7)
MeanSalinity <- c(mean_sal_EMs1, mean_sal_EMs7)
SDSalinity <- c(err_sal_EMs1, err_sal_EMs7)
n <- c(length(EMs1), length(EMs7))

write.csv(cbind(EM, MeanTemp, SDTemp,
                MeanSalinity, SDSalinity, n), "./mixing/sources_linear.csv",
          row.names = FALSE)

# load source data
source <- load_source_data(filename = "./mixing/sources_linear.csv",
                           source_factors = NULL, 
                           conc_dep = FALSE, 
                           data_type = "means", 
                           mix)

# create discrimination data: 0 because conservative parameters
MeanTemp <- rep(0, 2)
SDTemp <- rep(0, 2)
MeanSalinity <- rep(0, 2)
SDSalinity <- rep(0, 2)

write.csv(cbind(EM, MeanTemp, SDTemp,
                MeanSalinity, SDSalinity), "./mixing/discr_linear.csv",
          row.names = FALSE)

# load discrimination data
discr <- load_discr_data(filename = "./mixing/discr_linear.csv", mix)
```

## Make isospace plot & choose prior
```{r}
iso <- plot_data(filename = "isospace_plot", plot_save_pdf = FALSE,
                 plot_save_png = FALSE, mix, source, discr, return_obj = TRUE)
iso + theme(legend.position = "none")

calc_area(source = source, mix = mix, discr = discr) # 0

# uninformative (technically "generalist") prior (alpha = 1)
# Dirichlet distribution: all sources treated independently but must sum to 1 (Gelman et al. 2003)
plot_prior(alpha.prior = 1, source, plot_save_pdf = FALSE, plot_save_png = TRUE)
```

## Write model
```{r}
model_filename <- "./linear_model.txt"
resid_err <- FALSE # because n=1 per Station
process_err <- TRUE
write_JAGS_model(model_filename, resid_err, process_err, mix, source)

run <- list(chainLength = 3000000, burn = 1500000, thin = 500, chains = 3,
            calcDIC = TRUE)
jags.3 <- run_model(run, mix, source, discr, model_filename, alpha.prior = 1)
```

## Check for convergence
```{r}
output_options3 <- list(summary_save = TRUE,
                       summary_name = "summary_statistics3",
                       sup_post = TRUE,
                       plot_post_save_pdf = FALSE,
                       plot_post_name = "posterior_density3",
                       sup_pairs = TRUE,
                       plot_pairs_save_pdf = FALSE,
                       plot_pairs_name = "pairs_plot3",
                       sup_xy = FALSE,
                       plot_xy_save_pdf = FALSE,
                       plot_xy_name = "xy_plot3",
                       gelman = TRUE,
                       heidel = FALSE,
                       geweke = TRUE,
                       diag_save = TRUE,
                       diag_name = "diagnostics3",
                       indiv_effect = FALSE,
                       plot_post_save_png = FALSE,
                       plot_pairs_save_png = FALSE,
                       plot_xy_save_png = FALSE,
                       diag_save_ggmcmc = FALSE,
                       return_obj = TRUE)

options(max.print = 3000) # change global option
output_JAGS(jags.3, mix, source, output_options3)

diag <- output_diagnostics(jags.3, mix, source, output_options3)
df.stats <- output_stats(jags.3, mix, source, output_options3)
g.post <- output_posteriors(jags.3, mix, source, output_options3)

g.post$fac1[[1]]

# Gelman diagnostic should be < 1.05
# "extreme" MCMC parameters: 1; 0; 0

# Geweke diagnostic should have ~5% outside +/-1.96 (~31-32/634) in each chain
# "extreme" parameters: 34/22/24

```

## Plots for 3
```{r}
ggplot(oct[oct$Cast == "Surface", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM1)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()

ggplot(oct[oct$Cast == "Surface", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM7)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()


ggplot(oct[oct$Cast == "Surface", ]) +
  #geom_point(aes(x = a1, y = EM1)) +
  geom_text(aes(x = a1, y = EM1, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()

ggplot(oct[oct$Cast == "Surface", ]) +
  #geom_point(aes(x = a7, y = EM7)) +
  geom_text(aes(x = a7, y = EM7, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()
```

# Bottom: triangle

## Bayesian mixing model
```{r}
# create mixture data: bottom data w/ NAs excluded
read.csv("./data/OctCruiseData.csv") %>%
  rename(Temp = Temperature) %>%
  filter(Filtered == "",
         Cast == "Bottom",
         !is.na(Temp)) %>%
  select(-Filtered) %>%
  write_csv("./mixing/OctCruiseData_bottom.csv")

# load mixture data
mix <- load_mix_data(filename = "./mixing/OctCruiseData_bottom.csv", 
                     iso_names = c("Salinity", "Temp"),
                     factors = "Station",
                     fac_random = FALSE, # indiv. station is fixed effect
                     fac_nested = NULL,
                     cont_effects = NULL)

# create source data
EM <- c("EM4", "EM5", "EM6")
MeanTemp <- c(mean_temp_EMs4, mean_temp_EMs5, mean_temp_EMs6)
SDTemp <- c(err_temp_EMs4, err_temp_EMs5, err_temp_EMs6)
MeanSalinity <- c(mean_sal_EMs4, mean_sal_EMs5, mean_sal_EMs6)
SDSalinity <- c(err_sal_EMs4, err_sal_EMs5, err_sal_EMs6)
n <- c(length(EMs4), length(EMs5), length(EMs6))

write.csv(cbind(EM, MeanTemp, SDTemp,
                MeanSalinity, SDSalinity, n), "./mixing/sources_bottom.csv",
          row.names = FALSE)

# load source data
source <- load_source_data(filename = "./mixing/sources_bottom.csv",
                           source_factors = NULL, 
                           conc_dep = FALSE, 
                           data_type = "means", 
                           mix)

# create discrimination data: 0 because conservative parameters
MeanTemp <- rep(0, 3)
SDTemp <- rep(0, 3)
MeanSalinity <- rep(0, 3)
SDSalinity <- rep(0, 3)

write.csv(cbind(EM, MeanTemp, SDTemp,
                MeanSalinity, SDSalinity), "./mixing/discr_bottom.csv",
          row.names = FALSE)

# load discrimination data
discr <- load_discr_data(filename = "./mixing/discr_bottom.csv", mix)
```

## Make isospace plot & choose prior
```{r}
iso <- plot_data(filename = "isospace_plot", plot_save_pdf = FALSE,
                 plot_save_png = FALSE, mix, source, discr, return_obj = TRUE)
iso + theme(legend.position = "none")

calc_area(source = source, mix = mix, discr = discr) # 922.1111

# uninformative (technically "generalist") prior (alpha = 1)
# Dirichlet distribution: all sources treated independently but must sum to 1 (Gelman et al. 2003)
plot_prior(alpha.prior = 1, source, plot_save_pdf = FALSE, plot_save_png = TRUE)
```

## Write model
```{r}
model_filename <- "./bottom_model.txt"
resid_err <- FALSE # because n=1 per Station
process_err <- TRUE
write_JAGS_model(model_filename, resid_err, process_err, mix, source)

run <- list(chainLength = 3000000, burn = 1500000, thin = 500, chains = 3,
            calcDIC = TRUE)
jags.2 <- run_model(run, mix, source, discr, model_filename, alpha.prior = 1)
```

## Check for convergence
```{r}
output_options2 <- list(summary_save = TRUE,
                       summary_name = "summary_statistics2",
                       sup_post = TRUE,
                       plot_post_save_pdf = FALSE,
                       plot_post_name = "posterior_density2",
                       sup_pairs = TRUE,
                       plot_pairs_save_pdf = FALSE,
                       plot_pairs_name = "pairs_plot2",
                       sup_xy = FALSE,
                       plot_xy_save_pdf = FALSE,
                       plot_xy_name = "xy_plot2",
                       gelman = TRUE,
                       heidel = FALSE,
                       geweke = TRUE,
                       diag_save = TRUE,
                       diag_name = "diagnostics2",
                       indiv_effect = FALSE,
                       plot_post_save_png = FALSE,
                       plot_pairs_save_png = FALSE,
                       plot_xy_save_png = FALSE,
                       diag_save_ggmcmc = FALSE,
                       return_obj = TRUE)

options(max.print = 3000) # change global option
output_JAGS(jags.2, mix, source, output_options2)

diag <- output_diagnostics(jags.2, mix, source, output_options2)
df.stats <- output_stats(jags.2, mix, source, output_options2)
g.post <- output_posteriors(jags.2, mix, source, output_options2)

g.post$fac1[[1]]

# Gelman diagnostic should be < 1.05
# "extreme" MCMC parameters: 1; 0; 0
# EM6 = 076: 2; 0; 0

# Geweke diagnostic should have ~5% outside +/-1.96 (~31-32/634) in each chain
# "extreme" parameters: 34/22/24
# EM6 = 076: 38 / 37 / 29

```

## Plots for 2
```{r}
ggplot(oct[oct$Cast == "Bottom", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM4)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()

ggplot(oct[oct$Cast == "Bottom", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM5)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()

ggplot(oct[oct$Cast == "Bottom", ]) +
  geom_point(aes(x = Salinity, y = Temp, col = EM6)) +
  scale_colour_viridis(option = "viridis") +
  theme_bw()



ggplot(oct[oct$Cast == "Bottom", ]) +
  #geom_point(aes(x = a4, y = EM4)) +
  geom_text(aes(x = a4, y = EM4, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()


ggplot(oct[oct$Cast == "Bottom", ]) +
  #geom_point(aes(x = a5, y = EM5)) +
  geom_text(aes(x = a5, y = EM5, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()

ggplot(oct[oct$Cast == "Bottom", ]) +
  #geom_point(aes(x = a6, y = EM6)) +
  geom_text(aes(x = a6, y = EM6, label = Station)) +
  geom_abline(slope = 1) +
  theme_bw()
```




## *OLD* Calculate EM contributions
```{r}
oct$a1 <- NA
oct$a2 <- NA
oct$a3 <- NA
oct$a4 <- NA
oct$a5 <- NA
oct$a6 <- NA
oct$a7 <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface" &
     oct$Station[i] > "005") {
       oct$a3[i] = (oct$Salinity[i] - S1 - oct$Temp[i]*(S2-S1)/(T2-T1) +
             T1*(S2-S1)/(T2-T1)) /
            ((S3-S1) - (T3-T1)*(S2-S1)/(T2-T1))
       oct$a2[i] = (oct$Temp[i] - T1 - oct$a3[i]*(T3-T1)) / (T2-T1)
       oct$a1[i] = 1 - (oct$a2[i] + oct$a3[i])
     } else if(oct$Cast[i] == "Bottom") {
       oct$a6[i] = (oct$Salinity[i] - S4 - oct$Temp[i]*(S5-S4)/(T5-T4) +
             T4*(S5-S4)/(T5-T4)) /
            ((S6-S4) - (T6-T4)*(S5-S4)/(T5-T4))
       oct$a5[i] = (oct$Temp[i] - T4 - oct$a6[i]*(T6-T4)) / (T5-T4)
       oct$a4[i] = 1 - (oct$a5[i] + oct$a6[i])
     } else {
       oct$a7[i] = (oct$Salinity[i] - S1) / (S7 - S1)
       oct$a1[i] = 1 - oct$a7[i]
     }
}
```

## Calculate mixing-normalized DIC & TA values
```{r}
oct$DICn <- NA
oct$dDIC <- NA
oct$TAn <- NA
oct$dTA <- NA

## process used to solve the system of eq is at the end of this script

# a1*DIC1 + a2*DIC2 + a3*DIC3 = oct$DICn[i]
# a1*TA1 + a2*TA2 + a3*TA3 = oct$TAn[i]
# oct$DIC[i] - oct$DICn[i] = oct$dDICn[i]
# oct$TA[i] - oct$TAn[i] = oct$dTAn[i]

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface" &
     oct$Station[i] > "005") {
       oct$DICn[i] = oct$a1[i]*DIC1 + oct$a2[i]*DIC2 + oct$a3[i]*DIC3
       oct$dDIC[i] = oct$DIC[i] - oct$DICn[i]   # observed - expected
       oct$TAn[i] = oct$a1[i]*TA1 + oct$a2[i]*TA2 + oct$a3[i]*TA3
       oct$dTA[i] = oct$TA[i] - oct$TAn[i]   # observed - expected
     } else if(oct$Cast[i] == "Bottom") {
       oct$DICn[i] = oct$a4[i]*DIC4 + oct$a5[i]*DIC5 + oct$a6[i]*DIC6
       oct$dDIC[i] = oct$DIC[i] - oct$DICn[i]   # observed - expected
       oct$TAn[i] = oct$a4[i]*TA4 + oct$a5[i]*TA5 + oct$a6[i]*TA6
       oct$dTA[i] = oct$TA[i] - oct$TAn[i]   # observed - expected
     } else {
       oct$DICn[i] = oct$a1[i]*DIC1 + oct$a7[i]*DIC7
       oct$dDIC[i] = oct$DIC[i] - oct$DICn[i]   # observed - expected
       oct$TAn[i] = oct$a1[i]*TA1 + oct$a7[i]*TA7
       oct$dTA[i] = oct$TA[i] - oct$TAn[i]   # observed - expected
     }
}
```

## O2 mixing analysis
```{r}
DO1 <- oct$DO[EM1]
DO2 <- oct$DO[EM2]
DO3 <- oct$DO[EM3]

DO4 <- oct$DO[EM4]
DO5 <- oct$DO[EM5]
DO6 <- oct$DO[EM6]
DO7 <- oct$DO[EM7]

oct$DOn <- NA
oct$dDO <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface" &
     oct$Station[i] > "008") {
       oct$DOn[i] = oct$a1[i]*DO1 + oct$a2[i]*DO2 + oct$a3[i]*DO3
       oct$dDO[i] = oct$DO[i] - oct$DOn[i]   # observed - expected
     } else if(oct$Cast[i] == "Bottom") {
       oct$DOn[i] = oct$a4[i]*DO4 + oct$a5[i]*DO5 + oct$a6[i]*DO6
       oct$dDO[i] = oct$DO[i] - oct$DOn[i]   # observed - expected
     } else {
       oct$DOn[i] = oct$a1[i]*DO1 + oct$a7[i]*DO7
       oct$dDO[i] = oct$DO[i] - oct$DOn[i]   # observed - expected
     }
}
```

## Calculate CO2 atm equilibration time
```{r}
eqCO2sys <- carb(flag = 24,                               # pCO2 and ALK given
                 var1 = 420,
                 var2 = oct$TA / 10^6,                    # in mol/kg
                 S = oct$Salinity,
                 T = oct$Temp,
                 Patm = oct$Pressure * 0.098692326671601, # in atm
                 P = oct$SeaPressure / 10,                # in bar
                 k1k2 = "l",
                 ks = "d",
                 b = "l10")

oct$eqDIC <- NA
oct$d <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    oct$eqDIC[i] = eqCO2sys$DIC[i] * 10^6
    oct$d[i] = (oct$DIC[i] - oct$eqDIC[i]) /
                (oct$flux[i] / oct$MLD[i]) * oct$Density[i]
  }
}
```

## Calculate O2 atm equilibration time
```{r}
oct$d.O2 <- (oct$DO - oct$O2sol) / (oct$flux. / oct$MLD) * oct$Density
```

## Calculate eqDIC
```{r}
eqCO2sys <- carb(flag = 24,                               # pCO2 and ALK given
                 var1 = 420,
                 var2 = oct$TA[!is.na(oct$Temp)] / 10^6,                    # in mol/kg
                 S = oct$Salinity[!is.na(oct$Temp)],
                 T = oct$Temp[!is.na(oct$Temp)],
                 Patm = oct$Pressure[!is.na(oct$Temp)] * 0.098692326671601, # in atm
                 P = oct$SeaPressure[!is.na(oct$Temp)] / 10,                # in bar
                 k1k2 = "l",
                 ks = "d",
                 b = "l10")

oct$eqDIC <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    oct$eqDIC[i] = eqCO2sys$DIC[i] * 10^6
  }
}
```

## Look at dissolution-signal sites
```{r}
oct$dDIC.ex <- NA
oct$dTA.ex <- NA
oct$ratio <- NA

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Bottom" &
     !is.na(oct$dDIC[i]) &
     oct$dDIC[i] > median(oct$sdDICn, na.rm = T) &
     oct$dTA[i] > median(oct$sdTAn, na.rm = T)) {
    oct$dDIC.ex[i] <- oct$dDIC[i] - (oct$dDO[i] * 106/-138)
    oct$dTA.ex[i] <- oct$dTA[i] - (oct$dDO[i] * -17/-138)
    oct$ratio[i] <- oct$dTA.ex[i] / oct$dDIC.ex[i]
  }
}

oct %>%
  filter(Cast == "Bottom") %>%
ggplot() +
  geom_point(aes(x = dDIC.ex, y = dTA.ex, shape = Cast, col = "Oct")) +
  geom_abline(slope = 2, linetype = 2) +
  annotate("text", x = 32, y = 56, label = "2:1 line", fontface = 4) +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = "royalblue",
                      name = "Month") +
  theme_bw()

oct %>%
  filter(Cast == "Bottom") %>%
ggplot() +
  geom_point(aes(x = dDIC.ex, y = ratio, shape = Cast, col = "Oct")) +
  geom_hline(yintercept = 2, linetype = 2) +
  annotate("text", x = 30, y = 1.75, label = "TA:DIC = 2", fontface = 4) +
  ylab("Ratio of TA excess : DIC excess") +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = "royalblue",
                      name = "Month") +
  theme_bw()

oct %>%
  filter(Cast == "Bottom") %>%
ggplot() +
  geom_point(aes(x = OmegaAragonite, y = ratio, shape = Cast, col = "Oct")) +
  ylab("Ratio of TA excess : DIC excess") +
  scale_shape_manual(values = c(16, 1),
                     guide = guide_legend(reverse = TRUE)) +
  scale_colour_manual(values = "royalblue",
                      name = "Month") +
  theme_bw()
```
















## Bayesian initial attempts
```{r}
library(brms)

# Temp ~ rnorm(mu, sigma)

# set seed for repeatability
set.seed(1999)

# number of sims
n <- 1000

# random draws from the specified prior distributions
a <- rnorm(n, 33, 0.5)

ggplot(as.data.frame(a), aes(x = a)) +
  geom_histogram(binwidth = 0.1) +
  theme_bw()



b <- rnorm(n, mean_sal, sd_sal)

ggplot(as.data.frame(b), aes(x = b)) +
  geom_histogram(binwidth = 0.01) +
  theme_bw()

EM1dist <- a[a >= min_sal & a <= max_sal]

ggplot(table(EM1dist) / length(EM1dist), aes(x = EM1dist)) +
  geom_histogram() +
  theme_bw()

model_1 <-
  brm(data = oct$Salinity[oct$Cast == "Surface" &
                          oct$Station > "008"],
      family = gaussian,
    Salinity ~ 1 + b,
    prior = c(
      #prior(normal(75, 15), class = Intercept),
      #prior(lognormal(0, .8), class = b),
      prior(normal(mean_sal, 0.5), class = mean)
    ),
    iter = 41000, warmup = 40000, chains = 4, cores = 4,
    seed = 4
  )

oct$Salinity[oct$Station == "045" & oct$Cast == "Surface"] # 32.3097
oct$Salinity[oct$Station == "049" & oct$Cast == "Surface"] # 32.3717

S1_dist <- runif(1000, min = min(oct$Salinity[oct$Cast == "Surface"]),
                       max = max(oct$Salinity[oct$Cast == "Surface"]))

norm <- rnorm(100000, 32.33, 0.037)
within <- norm[norm >= oct$Salinity[oct$Station == "009" & oct$Cast == "Surface"] &
     norm <= oct$Salinity[oct$Station == "049" & oct$Cast == "Surface"]]

length(within) / length(norm) # 0.72967
```















## ResTime sensitivity analysis
```{r}
octResTime <- 63   # Brink et al. 2003
DICf63 <- as.vector(rep(NA, 228))

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    DICf63[i] = -1 * oct$flux[i] / oct$MLD[i] / oct$Density[i] * octResTime
  }
}

octResTime <- 20
DICf20 <- as.vector(rep(NA, 228))

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    DICf20[i] = -1 * oct$flux[i] / oct$MLD[i] / oct$Density[i] * octResTime
  }
}

fluxResTime <- as.data.frame(cbind(DICf20, DICf63))

octResTime <- 60
DICf60 <- as.vector(rep(NA, 228))

for(i in 1:nrow(oct)) {
  if(oct$Cast[i] == "Surface") {
    DICf60[i] = -1 * oct$flux[i] / oct$MLD[i] / oct$Density[i] * octResTime
  }
}

fluxResTime <- cbind(fluxResTime, DICf60)
```

## Identify end-members
```{r}
# surface
oct %>%
  filter(Cast == "Surface") %>%
  ggplot(aes(x = Salinity, y = Temp, shape = Cast, col = Cast)) +
    geom_text(aes(label = as.integer(Station)), size = 3) +
    scale_colour_manual(values = "coral2") +
    theme_bw()

# calling 5, 7, 43 EMs

# bottom
oct %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = Salinity, y = Temp, shape = Cast, col = Cast)) +
    geom_text(aes(label = as.integer(Station)), size = 3) +
    scale_colour_manual(values = "darkblue") +
    theme_bw()

# calling 9, 33, 53 EMs
```

## Convert AOU to DIC & TA signals --- NOT USING; FOUND BETTER METHOD
```{r}
# AOU umol/kg * 106 (DIC) / 138 (O2) = prod/resp DIC signal
oct$DICpr <- oct$AOU * 106 / 138

# AOU umol/kg * 17 (TA) / 138 (O2) = prod/resp TA signal
oct$TApr <- oct$AOU * 17 / 138
```

## Calculate "other" components of DIC & TA
```{r}
# DIC = DICn + DICpr + fDIC + other
# other = DIC - DICn - DICpr - fDIC
# other = DIC - DICn - DICpr (leaving out flux for bottom for now)

oct$DIC.other <- oct$DIC - oct$DICn - oct$DICpr

# TA = TAn + TApr + other
# other = TA - TAn - TApr

oct$TA.other = oct$TA - oct$TAn - oct$TApr

oct %>%
  filter(Cast == "Bottom") %>%
  ggplot(aes(x = DIC.other, y = TA.other)) +
  geom_point(aes(shape = Cast)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_abline(intercept = 0, slope = 2) +
  geom_abline(intercept = 0, slope = -17/106) +
  scale_shape_manual(values = c(16, 1)) +
  theme_bw()
```

## Solve system to find mixing-normalized coefficients
```{r}
i = 1

### SURFACE

### a1*S1 + a2*S2 + a3*S3 = oct$Salinity[i]
# a1 = (oct$Salinity[i] - (a2*S2 + a3*S3)) / S1
# 1 - (a2 + a3) = (oct$Salinity[i] - (a2*S2 + a3*S3)) / S1
# S1 - a2*S1 - a3*S1 = oct$Salinity[i] - a2*S2 - a3*S3
# a2*(S2-S1) + a3*(S3-S1) = oct$Salinity[i] - S1
# (oct$Temp[i] - T1 - a3*(T3-T1)) / (T2-T1) * (S2-S1) + a3*(S3-S1) = oct$Salinity[i] - S1
# a3*(S3-S1) - a3*(T3-T1)*(S2-S1)/(T2-T1) = oct$Salinity[i] - S1 - oct$Temp[i]*(S2-S1)/(T2-T1) + T1*(S2-S1)/(T2-T1)
a3 = (oct$Salinity[i] - S1 - oct$Temp[i]*(S2-S1)/(T2-T1) + T1*(S2-S1)/(T2-T1)) / ((S3-S1) - (T3-T1)*(S2-S1)/(T2-T1))

### a1*T1 + a2*T2 + a3*T3 = oct$Temp[i]
# a1 = (oct$Temp[i] - (a2*T2 + a3*T3)) / T1
# 1 - (a2 + a3) = (oct$Temp[i] - (a2*T2 + a3*T3)) / T1
# T1 - a2*T1 - a3*T1 = oct$Temp[i] - a2*T2 - a3*T3
# a2*(T2-T1) + a3*(T3-T1) = oct$Temp[i] - T1
a2 = (oct$Temp[i] - T1 - a3*(T3-T1)) / (T2-T1)

### a1 + a2 + a3 = 1
a1 = 1 - (a2 + a3)

### BOTTOM

a6 = (oct$Salinity[i] - S4 - oct$Temp[i]*(S5-S4)/(T5-T4) + T4*(S5-S4)/(T5-T4)) / ((S6-S4) - (T6-T4)*(S5-S4)/(T5-T4))

a5 = (oct$Temp[i] - T4 - a6*(T6-T4)) / (T5-T4)

a4 = 1 - (a5 + a6)
```
