---
title: "GeorgesBank_SAMs"
author: "Dylan Titmuss"
date: "9/30/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script creates a map of the planned October 2021 RSA stations overlaid on the 2020 SAM zones.

## Load packages
```{r}
library(tidyverse)
library(sf)
library(marmap)
library(nngeo)
library(ggmap)
library(cowplot)
```

## Register Google API key
```{r, include=FALSE}
register_google(key = "AIzaSyBn1OxFq4DMK79J4qHmQoBvFlbHbeImABw")
```

## Load GB shapefiles
```{r}
setwd("~/Desktop/Repos/ScallopRSA2021")
GB <- st_read("./data/2020SAMZones")

#st_is_valid(GB)

# subset shapefile to SAMs
NLS_North <- subset(GB, NewSAMS == "NLS-North")
CL1_South <- subset(GB, NewSAMS == "CL1-South")
CL1_Sliver <- subset(GB, NewSAMS == "CL1-Sliver")
CL2_AccessSoutheast <- subset(GB, NewSAMS == "CL2-Access-Southeast")
SF <- subset(GB, NewSAMS == "SF")
CL2_North <- subset(GB, NewSAMS == "CL2-North")
CL1_Access <- subset(GB, NewSAMS == "CL1-Access")
NF <- subset(GB, NewSAMS == "NF")
CL2_Ext <- subset(GB, NewSAMS == "CL2-Ext")
GSC <- subset(GB, NewSAMS == "GSC")
NLS_SouthDeep <- subset(GB, NewSAMS == "NLS-South-Deep")
NLS_West <- subset(GB, NewSAMS == "NLS-West")
NLS_SouthShallow <- subset(GB, NewSAMS == "NLS-South-Shallow")
CL2_AccessSouthwest <- subset(GB, NewSAMS == "CL2-Access-Southwest")
SF_East <- subset(GB, NewSAMS == "SF-East")

# combine polygons
GB_sf <- st_union(st_geometry(NLS_North), st_geometry(CL1_South)) %>%
  st_union(st_geometry(CL1_Sliver)) %>%
  st_union(st_geometry(CL2_AccessSoutheast)) %>%
  st_union(st_geometry(SF)) %>%
  st_union(st_geometry(CL2_North)) %>%
  st_union(st_geometry(CL1_Access)) %>%
  st_union(st_geometry(NF)) %>%
  st_union(st_geometry(CL2_Ext)) %>%
  st_union(st_geometry(GSC)) %>%
  st_union(st_geometry(NLS_SouthDeep)) %>%
  st_union(st_geometry(NLS_West)) %>%
  st_union(st_geometry(NLS_SouthShallow)) %>%
  st_union(st_geometry(CL2_AccessSouthwest)) %>%
  st_union(st_geometry(SF_East)) %>%
  st_remove_holes() # remove slivers between polygon borders
  
#summary(GB_sf)
```

## Create coastline polygon
```{r}
sf_use_s2(FALSE)

# get Massachusetts coastline
mass <- read_sf("/Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/library/gshhg-shp-2.3.7/GSHHS_shp/f/GSHHS_f_L1.shp") %>%
  st_make_valid() %>%
  st_crop(xmin = -74, xmax = -63, ymin = 38, ymax = 45)

# get state borders
borders <- read_sf("/Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/library/gshhg-shp-2.3.7/WDBII_shp/f/WDBII_border_f_L2.shp") %>%
  st_make_valid()

# test both
ggplot() +
  geom_sf(data = mass, fill = "darkgrey", colour = NA) +
  geom_sf(data = borders, colour = "black", linewidth = 0.2) +
  coord_sf(xlim = c(-73, -63.5),
           ylim = c(38, 44),
           crs = st_crs(4326))
```

## Load data
```{r}
oct <- read.csv("./data/OctCruiseData.csv") %>%
  rename(Lat = Latitude_degrees_start,
         Long = Longitude_degrees_start) %>%
  filter(Filtered == "", Cast == "Bottom") %>%
  mutate(Tow = ifelse(is.na(Tow_start_time), "N", "Y"))
```

## Convert coordinates from DM to DD
```{r}
chd <- substr(oct$Lat, 3, 3)[1]

# latitude
Lat_split_oct <- str_split_fixed(oct$Lat, chd, 2) %>%
                 as.data.frame()
Lat_split_oct$V2 <- str_remove_all(Lat_split_oct$V2, pattern = "'") %>%
                    as.numeric()
Lat_split_oct$V2 <- Lat_split_oct$V2/60
Lat_split_oct$V1 <- as.numeric(Lat_split_oct$V1)

oct$Lat <- Lat_split_oct$V1 + Lat_split_oct$V2
rm(Lat_split_oct)

# longitude
Long_split_oct <- str_split_fixed(oct$Long, chd, 2) %>%
                  as.data.frame()
Long_split_oct$V2 <- str_remove_all(Long_split_oct$V2, pattern = "'") %>%
                     as.numeric()
Long_split_oct$V2 <- Long_split_oct$V2/60
Long_split_oct$V1 <- as.numeric(Long_split_oct$V1)

oct$Long <- -(Long_split_oct$V1 + Long_split_oct$V2)
rm(Long_split_oct)
rm(chd)
```

## Create simple features obj of station data
```{r}
# create geometry column in data frame from lat/long data
for(i in 1:nrow(oct)) {
  oct$geometry[i] <- st_point(x = c(oct$Long[i], oct$Lat[i])) %>%
    st_sfc(crs = 4326)
}

# create an sf object from data frame
station_sf <- st_sf(oct, crs = 4326)
```

## Non-satellite maps
```{r}
# create base map with NOAA data
GB_bathy <- getNOAA.bathy(lon1 = -74, lon2 = -62,
lat1 = 37, lat2 = 46, resolution = 1)

# prepare for use with ggplot
ggbathy <- GB_bathy %>%
  fortify() %>%
  mutate(depth_bins = cut(z, breaks = c(0, -35, -55, -75, -95, -120, -200, -1000, -2000, -2500, -3000, -Inf)))

# zoomed out
EastCoast <- ggplot() +
  geom_raster(data = ggbathy, aes(x, y, fill = depth_bins), interpolate = TRUE, alpha = 0.75) +
  scale_fill_manual(values = c("#084184", "#08519C", "#1561A9", "#2171B5", "#3282BE", "#4292C6", "#57A0CE", "#6BAED6", "#85BCDC", "#9ECAE1", "#B2D3E8"),
                    na.value = "#B2D3E8") +
  geom_sf(data = mass, fill = "darkgrey", colour = "black", linewidth = 0.05) +
  geom_sf(data = borders, colour = "black", linewidth = 0.1) +
  geom_rect(aes(xmin = -70.5, xmax = -66, ymin = 40, ymax = 42.5),
            colour = "grey15", fill = alpha("grey", 0), linewidth = 0.5) +
  coord_sf(xlim = c(-73, -63.5), ylim = c(38, 44.5), crs = st_crs(4326)) +
  scale_x_continuous(breaks = c(-70, -66)) +
  scale_y_continuous(breaks = c(38, 40, 42, 44)) +
  theme_bw() +
  theme(axis.title = element_blank(),
        #axis.text = element_text(size = 6),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        plot.margin = margin(t = 3, r = 3, b = 0, l = 0),
        legend.position = "none")

# zoomed in
Georges <-
  ggplot() +
  geom_raster(data = ggbathy, aes(x, y, fill = depth_bins), interpolate = TRUE, alpha = 0.75) +
  scale_fill_manual(values = c("#084184", "#08519C", "#1561A9", "#2171B5", "#3282BE", "#4291C6", "#52A0CE", "#6BAFD6", "#84BDE4", "#9DD0EA", "#B5E2EF"),
                    na.value = "#B5DBEF",
                    breaks = levels(ggbathy$depth_bins)[1:11],
                    labels = c(">3000", "3000", "2500", "2000", "1000", "200",
                               "120", "95", "75", "55", "35"),
                    name = "Depth (m)") +
  geom_sf(data = GB_sf, fill = NA, colour = "black", linewidth = 0.4, linetype = "dashed") +
  geom_point(data = station_sf, aes(x = Long, y = Lat), shape = 17) +
  geom_sf(data = mass, fill = "darkgrey", colour = "black") +
  coord_sf(xlim = c(-70.5, -66), ylim = c(40, 42.5), crs = st_crs(4326)) +
  scale_y_continuous(breaks = c(40, 41, 42)) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_text(size = 12),
        legend.title = element_text(face = "bold"),
        legend.key.size = unit(0.45, "cm"),
        legend.position = c(1.1, 0.65)) +
  guides(fill = guide_legend(reverse = TRUE))

ggdraw(Georges) +
  draw_plot(EastCoast, x = 0.72, y = 0, width = 0.35, height = 0.35)
```

## Create map w/ SAMs and tow sites marked
```{r}
ggplot() +
  geom_raster(data = ggbathy, aes(x, y, fill = depth_bins), interpolate = TRUE, alpha = 0.75) +
  scale_fill_manual(values = c("#08306B", "#084184", "#08519C", "#1561A9", "#2171B5", "#3282BE", "#4292C6", "#57A0CE", "#6BAED6", "#85BCDC", "#9ECAE1", "#B2D3E8", "#C6DBEF"),
                    na.value = "#C6DBEF",
                    guide = "none") +
  geom_sf(data = GB_sf, fill = NA, colour = "black", linewidth = 0.4, linetype = "dashed") +
  geom_sf(data = mass, fill = "darkgrey", colour = "black") +
  geom_sf(data = NLS_North, fill = "palegreen2",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL1_South, fill = "firebrick3",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL1_Sliver, fill = "mediumorchid3",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_AccessSoutheast, fill = "lightskyblue",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = SF, fill = "darkorange2",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_North, fill = "seagreen2",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL1_Access, fill = "chartreuse3",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NF, fill = "peachpuff2",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_Ext, fill = "slateblue1",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = GSC, fill = "steelblue2",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NLS_SouthDeep, fill = "blueviolet",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NLS_West, fill = "lightpink2",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NLS_SouthShallow, fill = "tan3",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_AccessSouthwest, fill = "yellow2",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = SF_East, fill = "darkturquoise",
          alpha = 0.75, col = "transparent", inherit.aes = FALSE) +
  geom_point(data = station_sf, aes(x = Long, y = Lat, col = Tow), shape = 18, size = 4) +
  scale_colour_manual(values = c("black", "white"), labels = c("Towed", "Did not tow")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(breaks = c(40, 41, 42), expand = c(0, 0)) +
  coord_sf(xlim = c(-70.5, -66), ylim = c(40, 42.5), crs = st_crs(4326)) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_text(size = 14),
        legend.title = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 14),
        legend.position = "none") #+
  #guides(colour = guide_legend(title = "Scallop\nTow",
  #                             title.hjust = 0.5,
  #                             #reverse = TRUE,
  #                             override.aes = list(shape = c(23, 23),
  #                                                 col = c("black", "black"),
  #                                                 fill = c("white", "black"))))

```




## Using satellite map
```{r}
GB_map <- get_map(c(-68.5247, 40.8155), maptype = "satellite", zoom = 7, source = "google")

map <- ggmap(GB_map) +
  geom_sf(data = NLS_North, fill = "palegreen2", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL1_South, fill = "firebrick3", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL1_Sliver, fill = "mediumorchid3", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_AccessSoutheast, fill = "lightskyblue", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = SF, fill = "darkorange2", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_North, fill = "seagreen2", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL1_Access, fill = "chartreuse3", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NF, fill = "peachpuff2", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_Ext, fill = "slateblue1", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = GSC, fill = "steelblue1", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NLS_SouthDeep, fill = "blueviolet", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NLS_West, fill = "lightpink2", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = NLS_SouthShallow, fill = "tan3", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = CL2_AccessSouthwest, fill = "yellow2", col = "transparent", inherit.aes = FALSE) +
  geom_sf(data = SF_East, fill = "darkturquoise", col = "transparent", inherit.aes = FALSE) +
  coord_sf(crs = st_crs(4326)) +
  xlim(c(-70.5, -66)) +
  scale_y_continuous(breaks = c(40, 41, 42), limits = c(40, 42.5)) +
  theme(axis.title = element_blank())
map
```

## Load station data & convert coordinates
```{r}
stations <- read.csv("./data/CruiseTrack_October.csv")
str(stations)

chd <- substr(stations$Lat, 3, 4)[1]

# convert latitude from DM to DD
Lat_split <- str_split_fixed(stations$Lat, chd, 2) %>%
  as.data.frame()
Lat_split$V2 <- str_remove_all(Lat_split$V2, pattern = "'") %>%
  as.numeric()
Lat_split$V2 <- Lat_split$V2/60
Lat_split$V1 <- as.numeric(Lat_split$V1)

stations$Lat <- Lat_split$V1 + Lat_split$V2

# convert longitude from DM to DD
Long_split <- str_split_fixed(stations$Long, chd, 2) %>%
  as.data.frame()
Long_split$V2 <- str_remove_all(Long_split$V2, pattern = "'") %>%
  as.numeric()
Long_split$V2 <- Long_split$V2/60
Long_split$V1 <- as.numeric(Long_split$V1)

stations$Long <- -(Long_split$V1 + Long_split$V2)
```

## Add station points to map
```{r}
stations_SPDF <- SpatialPointsDataFrame(coords = stations[ , c("Long","Lat")],
                                        data = stations[ ,c("Long", "Lat", "Station", "Tow")],
                                        proj4string = CRS("+init=epsg:4326"))

stations_sf <- st_as_sf(stations_SPDF)
stations_sf <- st_transform(stations_sf, crs = 4326)

map +
  geom_sf(data = stations_sf, aes(color = Tow), inherit.aes = FALSE) +
  geom_sf_text(data = stations_sf, aes(label = Station), nudge_x = 0.034, nudge_y = 0.039, size = 2.5, inherit.aes = FALSE) +
  scale_colour_manual(values = c("black", "white")) +
  coord_sf(crs = st_crs(4326)) +
  theme(legend.position = "none")
```




## marmap version (no polygons)
```{r}
# Create base map with NOAA data
GB_bathy <- getNOAA.bathy(lon1 = -70.5, lon2 = -66,
lat1 = 40, lat2 = 42.5, resolution = 1)

summary(GB_bathy)

map <- plot(GB_bathy, image = TRUE, land = TRUE, n = 0, lwd = 1, bpal = list(c(min(GB_bathy), -175, "#08306B","#08519C", "#2171B5", "#4292C6"), 
            c(-175, 0, "#4292C6", "#6BAED6", "#9ECAE1", "#C6DBEF"), 
            c(0, max(GB_bathy), "grey")))
```

## raster version
```{r}
# fortify for use with ggplot
ggbathy <- GB_bathy %>%
  #fortify() %>%
  mutate(lat = y, long = x, depth = z) %>%
  select(-c(x, y, z)) %>%
  mutate(depth_bins = cut(depth, breaks = c(0, -30, -55, -75, -90, -120, -150, -180, -780, -1380, -1980, -2580, -3180, -Inf)))

ggplot() +
  geom_raster(data = ggbathy, aes(long, lat, fill = depth_bins), interpolate = TRUE, alpha = 0.75) +
  scale_fill_manual(values = c("#08306B", "#084184", "#08519C", "#1561A9", "#2171B5", "#3282BE", "#4292C6", "#57A0CE", "#6BAED6", "#85BCDC", "#9ECAE1", "#B2D3E8", "#C6DBEF")) +
  geom_sf(data = NLS_North, fill = "palegreen", col = "grey") +
  geom_sf(data = CL1_South, fill = "deepskyblue", col = "grey") +
  geom_sf(data = CL1_Sliver, fill = "mediumorchid1", col = "grey") +
  geom_sf(data = CL2_AccessSoutheast, fill = "goldenrod1", col = "grey") +
  geom_sf(data = SF, fill = "darkgrey", col = "grey") +
  geom_sf(data = CL2_North, fill = "orange", col = "grey") +
  geom_sf(data = CL1_Access, fill = "peachpuff", col = "grey") +
  geom_sf(data = NF, fill = "grey", col = "grey") +
  geom_sf(data = CL2_Ext, fill = "cyan", col = "grey") +
  geom_sf(data = GSC, fill = "navyblue", col = "grey") +
  geom_sf(data = NLS_SouthDeep, fill = "maroon", col = "grey") +
  geom_sf(data = NLS_West, fill = "darkgreen", col = "grey") +
  geom_sf(data = NLS_SouthShallow, fill = "limegreen", col = "grey") +
  geom_sf(data = CL2_AccessSouthwest, fill = "lightpink1", col = "grey") +
  geom_sf(data = SF_East, fill = "yellow", col = "grey") +
  coord_sf(crs = st_crs(4326)) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none")

# something funky happens with the coordinates when I try to add the shapefile -- not sure how to sort out the CRS

# oh fantastic, this one works too now
```

#### Playing around
st_crs(NLS_North)
NLS_North <- st_transform(NLS_North, crs = 4326)
st_crs(NLS_North)

## ggOceanMaps
```{r}
basemap(limits = c(-70.5, -66, 40, 42.5), grid.col = NA, bathymetry = TRUE, rotate = TRUE) +
  theme(legend.position = "none") +
  annotation_spatial(NLS_North, fill = "palegreen", col = "grey") +
  annotation_spatial(CL1_South, fill = "deepskyblue") +
  annotation_spatial(CL1_Sliver, fill = "mediumorchid1") +
  annotation_spatial(CL2_AccessSoutheast, fill = "goldenrod1") +
  annotation_spatial(SF, fill = "darkgrey") +
  annotation_spatial(CL2_North, fill = "orange") +
  annotation_spatial(CL1_Access, fill = "peachpuff") +
  annotation_spatial(NF, fill = "grey") +
  annotation_spatial(CL2_Ext, fill = "aquamarine1") +
  annotation_spatial(GSC, fill = "navyblue") +
  annotation_spatial(NLS_SouthDeep, fill = "maroon") +
  annotation_spatial(NLS_West, fill = "darkgreen") +
  annotation_spatial(NLS_SouthShallow, fill = "limegreen") +
  annotation_spatial(CL2_AccessSouthwest, fill = "lightpink1") +
  annotation_spatial(SF_East, fill = "yellow")
```

NLS_North
CL1_South
CL1_Sliver
CL2_AccessSoutheast
SF
CL2_North
CL1_Access
NF
CL2_Ext
GSC
NLS_SouthDeep
NLS_West
NLS_SouthShallow
CL2_AccessSouthwest
SF_East
